---
title: "Cover crop class"
output: html_document
date: "2023-02-06"
---

Notes:
Stephene Perry from Cornell Stats Consulting reccomends against additional statical tests on the likert scale data (5/22/2023). So the confidence intervals for overall satisfaction and multi-site design are just for fun...

#   Loading
```{r}
#Working directory should be changed to run on another computer, link to the folder where you download CoverCropSurvey2022_Cleaned.xlsx  
setwd("/Users/udm3/Library/CloudStorage/Box-Box/Cover Crops in Agroecosystems - Internal/Analysis/2022 Data (NSE overview paper analysis)")

library(openxlsx)
library(tidyverse)
library(maps)
library(ggrepel)
library(likert)
library(mmtable2)
library(patchwork)
library(grid)
library(ggplotify)

SurveyData1 <- read.xlsx("CoverCropSurvey2022_Cleaned.xlsx", sheet = 1)

SurveyDataFull <- SurveyData1 %>% 
  mutate(region = case_when(
    Q63 == "Cornell University" ~ "new york",
    Q63 == "Clemson University" ~ "south carolina",
    Q63 == "University of Nebraska" ~ "nebraska",
    Q63 == "University of Kentucky" ~ "kentucky",
    Q63 == "University of New Hampshire" ~ "new hampshire",
    Q63 == "Michigan State University" ~ "michigan"))

SurveyDataNamed <- SurveyDataFull
colnames(SurveyDataNamed) <- SurveyDataNamed[1,]
SurveyDataNamed <- SurveyDataNamed[-1,] 

SurveyDataFull[-1,] %>% 
  count(region)
```

#   Map of students
```{r}
us_states <- map_data("state")
 
SurveyDataState <- SurveyDataFull[-1,] %>% 
  count(region) %>% 
  arrange(n)

mean(SurveyDataState$n)
sd(SurveyDataState$n)

# merge and sort (plots in order, sort ensures states filled in)
Survey.geo <- left_join(us_states, SurveyDataState,by = "region")
Survey.geo <- Survey.geo[order(Survey.geo$order), ]


univ_data <- data.frame(
  university = c("Cornell", "Clemson", "UNL", 
                 "UK", "UNH", "MSU"),
  state = c("New York", "South Carolina", "Nebraska", "Kentucky", "New Hampshire", "Michigan"),
  lon = c(-76.48, -82.83, -96.67, -84.5, -71.54, -84.55),
  lat = c(42.45, 34.67, 40.82, 37.83, 43.2, 43.00))

#im excluding the confused UNL student here because we are reporting survey res
#tiff("Figs/SurveyDistribution.tiff",width = 6.06, height = 4.58, units = "in", res = 300)
ggplot(Survey.geo, aes(long, lat)) +
  geom_polygon(aes(group = group, fill = n),color = "black",linewidth = .275) +
  scale_fill_gradient(low = "cornflowerblue", high = "tomato2",
                      na.value = "grey95",breaks = c(3,4,8,12),
                      guide = guide_legend(keyheight = unit(6, units = "mm"),
                                          keywidth=unit(12, units = "mm")))+
  geom_point(data = univ_data, aes(x = lon, y = lat), color = "black", size = 2) +
  geom_label_repel(data = univ_data, aes(x = lon, y = lat, label = university),
            color = "black",box.padding = .6,
            fill = alpha("white",0.85)) +
  coord_fixed(1.3) +
  labs(#title = "Where are our students from?",
       #subtitle = "mean students at each site = 7 (std. devation = 3)",
       fill = "Number of survey responses")+
  theme_void()+
  theme(plot.title = element_text(size=25, face="bold",hjust = .2,vjust = -1),
        plot.subtitle = element_text(size=14,hjust = .15,vjust = -1),
        legend.position = "bottom",legend.text = element_text(size = 12))
#dev.off()
```

#   Overall Satisfaction
```{r}
SurveyData_likert1 <- SurveyDataNamed[,3:12]
SurveyData_likert1[1:10] <- lapply(SurveyData_likert1[1:10], factor)
SurveyData_likert1[2:10] <- lapply(SurveyData_likert1[2:10], factor,
                                   levels = c("Strongly Disagree","Disagree",
                                              "Unsure","Agree","Strongly Agree"))

names(SurveyData_likert1)[1] <- "University"
SurveyData_likert1 %>% 
  count(University) %>% 
  summarise(n=sum(n))

# Get the current column names of the data frame
SurveyData_likert1.col_names <- colnames(SurveyData_likert1)

# Remove the string "As a result of taking this course I can" from each column name
SurveyData_likert1.col_names_newTmp <- gsub("As a result of taking this course I can ", "",
                                          SurveyData_likert1.col_names)
SurveyData_likert1.col_names_newTmp <- str_to_sentence(SurveyData_likert1.col_names_newTmp)
SurveyData_likert1.col_names_new <- gsub("\\.", "",SurveyData_likert1.col_names_newTmp)

# Replace the original column names with the new names
colnames(SurveyData_likert1) <- SurveyData_likert1.col_names_new

# Plotting
## Overall
likert1.all <- likert(SurveyData_likert1[2:10]) 

#tiff("Figs/CourseRatings/OverallRating.tiff",width = 8.4, height = 7.22, units = "in", res = 300) #new is 840 x 722
plot(likert1.all, text.size=4.5,ordered = TRUE)+
  #labs(title = "As a result of taking this course, students can...",
   #    subtitle = "All sites (n = 43)")+
  theme_light(base_size = 16)+
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        legend.justification = 1)+
  scale_y_continuous(labels = abs, limits = c(-110, 130))
#dev.off()
```

```{r eval=FALSE, include=FALSE}
#Site-level

##  Cornell
SurveyData_likert1.Cornell<-SurveyData_likert1 %>% 
  filter(University == "Cornell University")
likert1.Cornell <- likert(SurveyData_likert1.Cornell[2:10]) 

tiff("Figs/CourseRatings/CornellRating.tiff",width = 9, height = 5.84, units = "in", res = 300)
plot(likert1.Cornell, ordered = TRUE)+
  labs(title = "As a result of taking this course, students can...",
       subtitle = "Cornell University (n = 8)")+
  theme(legend.title = element_blank())
dev.off()

##  Clemson
SurveyData_likert1.Clemson<-SurveyData_likert1 %>% 
  filter(University == "Clemson University")
likert1.Clemson <- likert(SurveyData_likert1.Clemson[2:10]) 

tiff("Figs/CourseRatings/ClemsonRating.tiff",width = 9, height = 5.84, units = "in", res = 300)
plot(likert1.Clemson,ordered = TRUE)+
  labs(title = "As a result of taking this course, students can...",
       subtitle = "Clemson University (n = 4)")+
  theme(legend.title = element_blank())
dev.off()

##  U_Nebraska
SurveyData_likert1.U_Nebraska<-SurveyData_likert1 %>% 
  filter(University == "University of Nebraska")
likert1.U_Nebraska <- likert(SurveyData_likert1.U_Nebraska[2:10]) 

tiff("Figs/CourseRatings/UNLRating.tiff",width = 9, height = 5.84, units = "in", res = 300)
plot(likert1.U_Nebraska, ordered = TRUE)+
  labs(title = "As a result of taking this course, students can...",
       subtitle = "University of Nebraska (n = 8)")+
  theme(legend.title = element_blank())
dev.off()

##  U_Kentucky - work on
SurveyData_likert1.UK<-SurveyData_likert1 %>% 
  filter(University == "University of Kentucky") 
likert1.U_Kentucky <- likert(SurveyData_likert1.UK[2:10]) 

tiff("Figs/CourseRatings/UKRating.tiff",width = 9, height = 5.84, units = "in", res = 300)
plot(likert1.U_Kentucky,ordered = TRUE)+
  labs(title = "As a result of taking this course, students can...",
       subtitle = "University of Kentucky (n = 8)")+
  theme(legend.title = element_blank())
dev.off()


##  UNH
SurveyData_likert1.UNH<-SurveyData_likert1 %>% 
  filter(University == "University of New Hampshire")
likert1.UNH <- likert(SurveyData_likert1.UNH[2:10])

tiff("Figs/CourseRatings/UNHRating.tiff",width = 9, height = 5.84, units = "in", res = 300)
plot(likert1.UNH, ordered = FALSE)+
  labs(title = "As a result of taking this course, students can...",
       subtitle = "University of New Hampshire (n = 3)")+
  theme(legend.title = element_blank())
dev.off()

##  Michigan State
SurveyData_likert1.MSU<-SurveyData_likert1 %>% 
  filter(University == "Michigan State University")
likert1.MSU <- likert(SurveyData_likert1.MSU[2:10]) 

tiff("Figs/CourseRatings/MSURating.tiff",width = 9, height = 5.84, units = "in", res = 300)
plot(likert1.MSU, ordered = TRUE)+
  labs(title = "As a result of taking this course, students can...",
       subtitle = "Michigan State University (n = 12)")+
  theme(legend.title = element_blank())
dev.off()

#Table
SurveyData_likert1_Table<-
  SurveyData_likert1 %>% 
    pivot_longer(2:10,names_to = "Question",values_to = "LikertValue") %>% 
    count(Question, University, LikertValue, .drop = F) %>% 
    mmtable(.,n) + 
        header_top(Question) +
        header_left(LikertValue) + 
        header_left_top(University)
SurveyData_likert1_Table
```
```{r eval=FALSE, include=FALSE}
#Confidence intervals

# Making the binomial test loop
## cut =cutoff point
## z = baseline of average satisfaction

satisfied_ci<-function(x,score=cut,baseline=z){
  satisfied<-(x>score)*1 
  n<-length(x)
  p<-sum(satisfied)
  mid<-round(p/n*100,0)
  b<-binom.test(p,n,baseline, alternative = "two.sided")
  c(mid,round(b$conf.int*100,0),round(b$p.value,3))
}

# Data prep
Likert1_CI<-SurveyData_likert1 %>% 
  pivot_longer(2:10,names_to = "Question",values_to = "ResponseValue")

Likert1_CI$ResponseValue <- as.numeric(Likert1_CI$ResponseValue)
unique(Likert1_CI$Question)

# Testing - confirmed that the same results as website 5/17/23
cut<-3 #cutoff point
z<-sum(Likert1_CI$ResponseValue>cut)/length(Likert1_CI$ResponseValue) #baseline of average satisfaction

dd <- Likert1_CI %>% group_by(Question)%>% 
  summarise(lwr=satisfied_ci(ResponseValue,score = cut,baseline = z)[2],
            med=satisfied_ci(ResponseValue,score = cut,baseline = z)[1],
            upr=satisfied_ci(ResponseValue,score = cut,baseline = z)[3],
            n=n(),
            n_sat=sum((ResponseValue>3)*1),
            p_val=satisfied_ci(ResponseValue,score = cut,baseline = z)[4])

dd<-dd[order(dd$med),]
dd$Question = factor(dd$Question, levels=dd$Question[order(dd$med)], ordered=TRUE)
#dd<-subset(dd,dd$med>90)
ggplot(dd,aes(x=Question))+
  geom_point(aes(y=med),colour="red",size=2)+
  geom_hline(yintercept=z*100,
             col="red",size = 1.5,linetype="dashed") +
  geom_errorbar(aes(ymin=lwr,ymax=upr,width = .75))+
  coord_flip()+
  labs(title = "As a result of taking this course, students can...",
       y = "Percent agreement",
       subtitle = "All sites (n = 43)")+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 50))+
  theme(plot.title = element_text(size=25, face="bold",hjust = .2,vjust = -1),
        plot.subtitle = element_text(size=14,hjust = .15,vjust = -1),
        legend.position = "bottom",legend.text = element_text(size = 12))+
  theme_bw()
```
```{r eval=FALSE, include=FALSE}
#Viz
#Likert
Satisfaction1<-
  plot(likert1.all, ordered = TRUE)+
      theme_bw()+
      theme(legend.title = element_blank(),
            legend.position = "bottom",
            legend.text = element_text(size = 10))
#Binomial
levels(dd$Question)
dd$Question <- factor(dd$Question,
                      levels=(dd$Question)[rev(c(8,9,6,7,4,5,3,2,1))])

Satisfaction2<-
  ggplot(dd,aes(x=Question))+
    geom_point(aes(y=med,shape="Observed agreement"),size=2)+
    geom_hline(aes(yintercept=z*100,color = "Average agreement over all questions"),size = 1.5,linetype="dashed") +
    geom_errorbar(aes(ymin=lwr,ymax=upr,width = .75))+
    scale_color_discrete(name = "")+
    scale_shape_discrete(name = "")+
    coord_flip()+
    labs(y = "Percent agreement")+
    theme_bw()+
    theme(axis.text.y = element_blank(),
          axis.title.y = element_blank(),
          legend.position = "bottom",
          legend.text = element_text(size = 10))

SatisfactionComb <- Satisfaction1 + Satisfaction2 +
  plot_annotation(
    title = "As a result of taking this course, students can...",
    theme = theme(plot.title = element_text(size = 16)))

SatisfactionComb
```

#   Multi-site design
```{r}
SurveyData_likert2 <- SurveyDataNamed[,c(3,14:16)]
SurveyData_likert2[1:4] <- lapply(SurveyData_likert2[1:4], factor)
SurveyData_likert2[2:4] <- lapply(SurveyData_likert2[2:4], factor,
                                   levels = c("Strongly Disagree","Disagree",
                                              "Unsure","Agree","Strongly Agree"))

names(SurveyData_likert2)[1] <- "University"
SurveyData_likert2 %>% 
  count(University)

#Removing UK from questions due to the alternative lecture format. Erin Harimoto approved 5/17/2023:
##  Having instructors from other regions and institutions was a valuable part of recorded lectures
##  Indicate your level of agreement or disagreement with the following: - I would have preferred the lectures be delivered synchronously (live via Zoom or in-person)
SurveyData_likert2[
  SurveyData_likert2$University == "University of Kentucky",
  c("Having instructors from other regions and institutions was a valuable part of recorded lectures",
    "I would have preferred the lectures be delivered synchronously (live via Zoom or in-person)")]<- NA


# Plotting
## Overall
likert2.all <- likert(SurveyData_likert2[2:4]) 

#tiff("Figs/Multi-siteDesign/DesignOverll.tiff",width = 8.4, height = 5.31, units = "in", res = 300)
plot(likert2.all, text.size=4.5, ordered = TRUE)+
  #labs(title = "Multi-site design",
       #subtitle = "All sites (n = 43), Question 2\nExcluding University of Kentucky (n = 35), Question 1 & 3")+
  theme_light(base_size = 16)+
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        legend.justification = 1)+
  scale_y_continuous(labels = abs, limits = c(-112, 116.5))
#dev.off()
```

```{r eval=FALSE, include=FALSE}
#Site-level


##  Cornell
SurveyData_likert2.Cornell<-SurveyData_likert2 %>% 
  filter(University == "Cornell University")
likert2.Cornell <- likert(SurveyData_likert2.Cornell[2:4]) 

tiff("Figs/Multi-siteDesign/DesignCornell.tiff",width = 9, height = 5.84, units = "in", res = 300)
plot(likert2.Cornell, ordered = FALSE)+
  labs(title = "Multi-site design",
       subtitle = "Cornell University (n = 8)")+
  theme(legend.title = element_blank())
dev.off()

##  Clemson
SurveyData_likert2.Clemson<-SurveyData_likert2 %>% 
  filter(University == "Clemson University")
likert2.Clemson <- likert(SurveyData_likert2.Clemson[2:4]) 

tiff("Figs/Multi-siteDesign/DesignClemson.tiff",width = 9, height = 5.84, units = "in", res = 300)
plot(likert2.Clemson,ordered = FALSE)+
  labs(title = "Multi-site design",
       subtitle = "Clemson University (n = 4)")+
  theme(legend.title = element_blank())
dev.off()

##  U_Nebraska
SurveyData_likert2.U_Nebraska<-SurveyData_likert2 %>% 
  filter(University == "University of Nebraska")
likert2.U_Nebraska <- likert(SurveyData_likert2.U_Nebraska[2:4]) 

tiff("Figs/Multi-siteDesign/DesignUNL.tiff",width = 9, height = 5.84, units = "in", res = 300)
plot(likert2.U_Nebraska, ordered = FALSE)+
  labs(title = "Multi-site design",
       subtitle = "University of Nebraska (n = 8)")+
  theme(legend.title = element_blank())
dev.off()

##  U_Kentucky - work on
SurveyData_likert2.UK<-SurveyData_likert2 %>% 
  filter(University == "University of Kentucky") 
likert2.U_Kentucky <- likert(SurveyData_likert2.UK[2:4]) 

tiff("Figs/Multi-siteDesign/DesignUK.tiff",width = 9, height = 5.84, units = "in", res = 300)
plot(likert2.U_Kentucky,ordered = FALSE)+
  labs(title = "Multi-site design",
       subtitle = "University of Kentucky (n = 8)")+
  theme(legend.title = element_blank())
dev.off()

##  UNH
SurveyData_likert2.UNH<-SurveyData_likert2 %>% 
  filter(University == "University of New Hampshire")
likert2.UNH <- likert(SurveyData_likert2.UNH[2:4]) 

tiff("Figs/Multi-siteDesign/DesignUNH.tiff",width = 9, height = 5.84, units = "in", res = 300)
plot(likert2.UNH, ordered = FALSE)+
  labs(title = "Multi-site design",
       subtitle = "University of New Hampshire (n = 3)")+
  theme(legend.title = element_blank())
dev.off()

##  Michigan State
SurveyData_likert2.MSU<-SurveyData_likert2 %>% 
  filter(University == "Michigan State University")
likert2.MSU <- likert(SurveyData_likert2.MSU[2:4])

tiff("Figs/Multi-siteDesign/DesignMSU.tiff",width = 9, height = 5.84, units = "in", res = 300)
plot(likert2.MSU, ordered = FALSE)+
  labs(title = "Multi-site design",
       subtitle = "Michigan State University (n = 12)")+
  theme(legend.title = element_blank())
dev.off()

#Table
SurveyData_likert2_Table<-
  SurveyData_likert2 %>% 
    pivot_longer(2:4,names_to = "Question",values_to = "LikertValue") %>% 
    count(Question, University, LikertValue, .drop = F) %>% 
    mmtable(.,n) + 
        header_top(Question) +
        header_left(LikertValue) + 
        header_left_top(University)
SurveyData_likert2_Table
```
```{r eval=FALSE, include=FALSE}
#Confidence intervals


# Making the binomial test loop
## cut_2 =cutoff point for multi-site design
## z_2 = baseline of average satisfaction for multi-site design
satisfied_ci_2<-function(x,score=cut_2,baseline=z_2){
  satisfied<-(x>score)*1 
  n<-length(x)
  p<-sum(satisfied)
  mid<-round(p/n*100,0)
  b<-binom.test(p,n,baseline, alternative = "two.sided")
  c(mid,round(b$conf.int*100,0),round(b$p.value,3))
}

# Data prep
Likert2_CI<-SurveyData_likert2 %>% 
  pivot_longer(2:4,names_to = "Question",values_to = "ResponseValue")

Likert2_CI$ResponseValue <- as.numeric(Likert2_CI$ResponseValue)
unique(Likert2_CI$Question)

cut_2<-3 #cutoff point
z_2<-sum(Likert2_CI$ResponseValue>cut,na.rm = TRUE)/length(na.omit(Likert2_CI$ResponseValue)) #baseline of average satisfaction

dd_2 <- Likert2_CI %>% group_by(Question)%>% na.omit() %>% 
  summarise(lwr=satisfied_ci_2(ResponseValue,score = cut_2,baseline = z_2)[2],
            med=satisfied_ci_2(ResponseValue,score = cut_2,baseline = z_2)[1],
            upr=satisfied_ci_2(ResponseValue,score = cut_2,baseline = z_2)[3],
            n=n(),
            n_sat=sum((ResponseValue>3)*1),
            p_val=satisfied_ci_2(ResponseValue,score = cut_2,baseline = z_2)[4])

#confirming that na.omit worked - looks good! 5/19/2023
Likert2_CI %>% 
  filter(
    Question == "Having instructors from other regions and institutions was a valuable part of recorded lectures") %>% 
  na.omit() %>% #correctly omitted 8 UK students
    summarise(lwr=satisfied_ci_2(ResponseValue,score = cut_2,baseline = z_2)[2],
            med=satisfied_ci_2(ResponseValue,score = cut_2,baseline = z_2)[1],
            upr=satisfied_ci_2(ResponseValue,score = cut_2,baseline = z_2)[3],
            n=n(),
            n_sat=sum((ResponseValue>3)*1),
            p_val=satisfied_ci_2(ResponseValue,score = cut_2,baseline = z_2)[4])


dd_2<-dd_2[order(dd_2$med),]
dd_2$Question = factor(dd_2$Question, levels=dd_2$Question[order(dd_2$med)], ordered=TRUE)

ggplot(dd_2,aes(x=Question))+
  geom_point(aes(y=med),colour="red",size=2)+
  geom_hline(yintercept=z_2*100,
             col="red",size = 1.5,linetype="dashed") +
  geom_errorbar(aes(ymin=lwr,ymax=upr,width = .75))+
  coord_flip()+
  labs(title = "As a result of taking this course, students can...",
       y = "Percent agreement",
       subtitle = "All sites (n = 43), Question 2\nExcluding University of Kentucky (n = 35), Question 1 & 3")+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 50))+
  theme(plot.title = element_text(size=25, face="bold",hjust = .2,vjust = -1),
        plot.subtitle = element_text(size=14,hjust = .15,vjust = -1),
        legend.position = "bottom",legend.text = element_text(size = 12))+
  theme_bw()
```
```{r eval=FALSE, include=FALSE}
#Viz
MultiSiteDes_1<-
  plot(likert2.all, ordered = TRUE)+
      theme_bw()+
      theme(legend.title = element_blank(),
            legend.position = "bottom",
            legend.text = element_text(size = 10))

MultiSiteDes_2<-
  ggplot(dd_2,aes(x=Question))+
    geom_point(aes(y=med,shape="Observed agreement"),size=2)+
    geom_hline(aes(yintercept=z_2*100,color = "Average agreement over all questions"),
               size = 1.5,linetype="dashed") +
    geom_errorbar(aes(ymin=lwr,ymax=upr,width = .75))+
    scale_color_discrete(name = "")+
    scale_shape_discrete(name = "")+
    coord_flip()+
    labs(y = "Percent agreement")+
    scale_x_discrete(labels = function(x) str_wrap(x, width = 50))+
    theme_bw()+
    theme(axis.text.y = element_blank(),
          axis.title.y = element_blank(),
          legend.position = "bottom",
          legend.text = element_text(size = 10))

MultiSiteDesComb <- MultiSiteDes_1 + MultiSiteDes_2 +
  plot_annotation(
    title = "Students' review of multi-site course design",
    theme = theme(plot.title = element_text(size = 16)))

MultiSiteDesComb
```

#   Lab effectivness
```{r}
SurveyData_binary1 <- SurveyDataNamed[,c(3,18:19)]

FactorNames <- c("Module 1: CropScape and Web Soil Survey",
                                              "Module 2: Cover crop challenge: start",
                                              "Module 3: Cover crop emergence: seed size x planting depth",
                                              "Module 4: Cover crop ground cover: species x planting rate",
                                              "Module 5: Online mixture calculators",
                                              "Module 7: Soil health activities and exercises",
                                              "Module 8: Cover crop challenge: harvest and multifunctionality",
                                              "Module 9: Cover crop challenge: weighing samples",
                                              "Module 10: Cover crop innovations: introduction",
                                              "Module 11: Cover crop partial budgets",
                                              "Module 12: Town hall preparation",
                                              "Module 13: Cover crop innovations: presentations")


unique(SurveyData_binary1[,2]) %in% FactorNames #NA not present but that's okay
unique(SurveyData_binary1[,3]) %in% FactorNames #NA not present but that's okay

SurveyData_binary1[1:3] <- lapply(SurveyData_binary1[1:3], factor)
SurveyData_binary1[2:3] <- lapply(SurveyData_binary1[2:3], factor,
                                   levels = c("Module 1: CropScape and Web Soil Survey",
                                              "Module 2: Cover crop challenge: start",
                                              "Module 3: Cover crop emergence: seed size x planting depth",
                                              "Module 4: Cover crop ground cover: species x planting rate",
                                              "Module 5: Online mixture calculators",
                                              "Module 7: Soil health activities and exercises",
                                              "Module 8: Cover crop challenge: harvest and multifunctionality",
                                              "Module 9: Cover crop challenge: weighing samples",
                                              "Module 10: Cover crop innovations: introduction",
                                              "Module 11: Cover crop partial budgets",
                                              "Module 12: Town hall preparation",
                                              "Module 13: Cover crop innovations: presentations"),
                                  labels = c("Module 1: CropScape and Web Soil Survey",
                                              "Module 2: Cover crop challenge: Start",
                                              "Module 3: Cover crop emergence: Seed size x planting depth",
                                              "Module 4: Cover crop ground cover: Species x planting rate",
                                              "Module 5: Online mixture calculators",
                                              "Module 7: Soil health activities and exercises",
                                              "Module 8: Cover crop challenge: Harvest and multifunctionality",
                                              "Module 9: Cover crop challenge: Weighing samples",
                                              "Module 10: Cover crop innovations: Introduction",
                                              "Module 11: Cover crop partial budgets",
                                              "Module 12: Town hall preparation",
                                              "Module 13: Cover crop innovations: Presentations"))

names(SurveyData_binary1)[1] <- "University"
names(SurveyData_binary1)[2] <- "MostEffective"
names(SurveyData_binary1)[3] <- "LeastEffective"

SurveyData_binary1a<-
  SurveyData_binary1 %>% 
    count(University,MostEffective,.drop = FALSE) %>% 
    rename(Module = MostEffective, MostEffective = n)

SurveyData_binary1b<-
  SurveyData_binary1 %>% 
    count(University,LeastEffective,.drop = FALSE) %>% 
    rename(Module = LeastEffective, LeastEffective = n)

SurveyData_binary1.Full.a <- left_join(SurveyData_binary1a,SurveyData_binary1b)

#Overall
SurveyData_binary1.FullOverall.a <-
  SurveyData_binary1 %>% 
    drop_na(MostEffective) %>%  
    count(MostEffective,.drop = FALSE) %>% 
    rename(Module = MostEffective, MostEffective = n) %>% 
    mutate(Pct_Most = MostEffective/sum(MostEffective))

SurveyData_binary1.FullOverall.b <-
  SurveyData_binary1 %>% 
    drop_na(LeastEffective) %>% 
    count(LeastEffective,.drop = FALSE) %>% 
    rename(Module = LeastEffective, LeastEffective = n) %>% 
    mutate(Pct_Least = -1*LeastEffective/sum(LeastEffective))


SurveyData_binary1.FullOverallTmp <- full_join(SurveyData_binary1.FullOverall.a,
                                               SurveyData_binary1.FullOverall.b)

SurveyData_binary1.FullOverall <-
  SurveyData_binary1.FullOverallTmp %>% 
    select(-c(MostEffective,LeastEffective)) %>% 
    pivot_longer(c(Pct_Most,Pct_Least), names_to = "Response",values_to = "Pct")

LabValues <- SurveyData_binary1.FullOverall %>% 
  group_by(Module) %>% 
  summarise(Pct_Most = sum(Pct[Pct > 0],na.rm = TRUE)*100,
            Pct_Least = sum(Pct[Pct < 0],na.rm = TRUE)*100) %>% 
  arrange(-Pct_Most,-Pct_Least)

SurveyData_binary1.FullOverall.a$Module <-
  factor(SurveyData_binary1.FullOverall.a$Module,levels = LabValues$Module)
SurveyData_binary1.FullOverall.b$Module <-
  factor(SurveyData_binary1.FullOverall.b$Module,levels = LabValues$Module)

#tiff("Figs/LabRatings/LabRatingsOverall.tiff",width = 9.00, height = 5.31, units = "in", res = 300)
ggplot()+
  geom_bar(data = SurveyData_binary1.FullOverall.a,
           aes(x = Module,y = Pct_Most,fill = 'Most effective'),
           stat = "identity")+
  geom_text(data = SurveyData_binary1.FullOverall.a, size = 4.12,
            aes(x = Module,y= 0.30,
                label=scales::percent(round(Pct_Most,2))))+
  geom_bar(data = SurveyData_binary1.FullOverall.b,
           aes(x = Module,y = Pct_Least,fill = 'Least effective'),
           stat = "identity")+
  geom_text(data = SurveyData_binary1.FullOverall.b, size = 4.12,
            aes(x = Module,y= -0.22,
                label=scales::percent(abs(round(Pct_Least,2)))))+
  scale_x_discrete(limits=rev)+
  coord_flip()+
  geom_hline(yintercept=0, color = "black", size=.2)+
  labs(x = NULL,y = "Percentage", fill = NULL)+
       #title = "Lab effectiveness - All sites")+
  scale_y_continuous(breaks=c(-.20,-.10,0,.10,.20,.30),
                     labels=c('20', '10', '0',"10","20","30"))+
  scale_fill_brewer(palette = "Accent",
                    labels=c('Least effective', 'Most effective'), direction = -1)+
  theme_light(base_size = 16)+
  theme(legend.position = "bottom")
#dev.off()
```

```{r, eval=FALSE, include=FALSE}
#Site-specific
SurveyData_binary1.Full.b <- 
  SurveyData_binary1.Full.a %>% 
  group_by(University) %>% 
  summarize(Pct_Most = MostEffective/sum(MostEffective),
            Pct_Least = -1*LeastEffective/sum(LeastEffective))

SurveyData_binary1.FullTmp <- cbind(SurveyData_binary1.Full.a,SurveyData_binary1.Full.b[,2:3])

SurveyData_binary1.Full <-
  SurveyData_binary1.FullTmp %>% 
    filter(!is.na(Module)) %>% 
    select(-c(MostEffective,LeastEffective)) %>% 
    pivot_longer(c(Pct_Most,Pct_Least), names_to = "Response",values_to = "Pct")

tiff("Figs/LabRatings/LabRatingsSites.tiff",width = 8.77, height = 5.52, units = "in", res = 300)
ggplot(SurveyData_binary1.Full, aes(Module, Pct, fill = Response))+
  coord_flip()+
  geom_bar(stat = "identity")+
  geom_hline(yintercept=0, color = "white", size=.2)+
  labs(x = NULL,y = NULL, fill = NULL)+
  scale_x_discrete(limits=rev)+
  scale_y_continuous(breaks=c(-1,-.5,0,.5,1), labels=c('100%', '50%', '0%',"50%","100%"))+
  scale_fill_brewer(palette = "Accent", labels=c('Least effective', 'Most effective'),direction = -1)+
  facet_wrap(~University)+
  theme_light()+
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1))
dev.off()
```

#   Multi-site activity
```{r}
SurveyData_binary2 <- SurveyDataNamed[,c(3,20:21)]
SurveyData_binary2[1:3] <- lapply(SurveyData_binary2[1:3], factor)

names(SurveyData_binary2)[1] <- "University"
names(SurveyData_binary2)[2] <- "MostEffective"
names(SurveyData_binary2)[3] <- "LeastEffective"  

which(unique(SurveyData_binary2$MostEffective) %in% unique(SurveyData_binary2$LeastEffective)==FALSE)

SurveyData_binary2[2:3] <- lapply(SurveyData_binary2[2:3], factor,
                                   levels = c("1. Course introduction and regional differences",
                                              "2. Cover crop selector tools",
                                              "3. Fitting cover crops into rotation: rotation design",
                                              "4. Fitting cover crops into rotation: adding cover crops",
                                              "5. Fitting cover crops into rotation: termination options",
                                              "6. Soil health sampling and testing",
                                              "7. Spider plot activity from cover crop challenge",
                                              "8. Cover crops and soil N",
                                              "9. Farmer innovator panel",
                                              "10. cover crop challenge results",
                                              "11. Town hall role-playing",
                                              "12. Innovator presentations"),
                                  labels = c("Module 1: Course introduction and regional differences",
                                              "Module 2: Cover crop selector tools",
                                              "Module 3: Fitting cover crops into rotation: Rotation design",
                                              "Module 4: Fitting cover crops into rotation: Adding cover crops",
                                              "Module 5: Fitting cover crops into rotation: Termination options",
                                              "Module 7: Soil health sampling and testing",
                                              "Module 8: Spider plot activity from cover crop challenge",
                                              "Module 9: Cover crops and soil N",
                                              "Module 10: Farmer innovator panel",
                                              "Module 11: Cover crop challenge results",
                                              "Module 12: Town hall role-playing",
                                              "Module 13: Innovator presentations"))

#SurveyData_binary2<-SurveyData_binary2 %>% 
 # mutate(MostEffective = paste("Module ", MostEffective, sep = ""),
  #       LeastEffective = paste("Module ", LeastEffective, sep = ""),
   #      across(c(MostEffective, LeastEffective), ~str_replace_all(., "\\.", ":")),
    #     across(c(MostEffective, LeastEffective), na_if,"Module NA"))
#SurveyData_binary2<-droplevels(SurveyData_binary2)

SurveyData_binary2a<-
  SurveyData_binary2 %>% 
    count(University,MostEffective,.drop = FALSE) %>% 
    rename(Module = MostEffective, MostEffective = n)

SurveyData_binary2b<-
  SurveyData_binary2 %>% 
    count(University,LeastEffective,.drop = FALSE) %>% 
    rename(Module = LeastEffective, LeastEffective = n)

SurveyData_binary2.Full.a <- left_join(SurveyData_binary2a,SurveyData_binary2b)

##  Overall
SurveyData_binary2.FullOverall.a <-
  SurveyData_binary2 %>% 
    drop_na(MostEffective) %>% 
    count(MostEffective,.drop = FALSE) %>% 
    rename(Module = MostEffective, MostEffective = n) %>% 
    mutate(Pct_Most = MostEffective/sum(MostEffective))

SurveyData_binary2.FullOverall.b <-
  SurveyData_binary2 %>% 
    drop_na(LeastEffective) %>%
    count(LeastEffective,.drop = FALSE) %>% 
    rename(Module = LeastEffective, LeastEffective = n) %>% 
    mutate(Pct_Least = -1*LeastEffective/sum(LeastEffective))

SurveyData_binary2.FullOverallTmp <- full_join(SurveyData_binary2.FullOverall.a,
                                               SurveyData_binary2.FullOverall.b)

SurveyData_binary2.FullOverall <-
  SurveyData_binary2.FullOverallTmp %>% 
    select(-c(MostEffective,LeastEffective)) %>% 
    pivot_longer(c(Pct_Most,Pct_Least), names_to = "Response",values_to = "Pct")

LabValues_Multi <- SurveyData_binary2.FullOverall %>% 
  group_by(Module) %>% 
  summarise(Pct_Most = sum(Pct[Pct > 0],na.rm = TRUE)*100,
            Pct_Least = sum(Pct[Pct < 0],na.rm = TRUE)*100) %>% 
  arrange(-Pct_Most,-Pct_Least)

SurveyData_binary2.FullOverall.a$Module <-
  factor(SurveyData_binary2.FullOverall.a$Module,levels = LabValues_Multi$Module)
SurveyData_binary2.FullOverall.b$Module <-
  factor(SurveyData_binary2.FullOverall.b$Module,levels = LabValues_Multi$Module)

#tiff("Figs/Multi-siteMeetings/Multi-siteMeetingsOverall.tiff",width = 9, height = 5.31, units = "in", res = 300)
ggplot()+
  geom_bar(data = SurveyData_binary2.FullOverall.a,
           aes(x = Module,y = Pct_Most,fill = 'Most effective'),
           stat = "identity")+
  geom_text(data = SurveyData_binary2.FullOverall.a, size = 4.12,
            aes(x = Module,y= 0.35,
                label=scales::percent(round(Pct_Most,2))))+
  geom_bar(data = SurveyData_binary2.FullOverall.b,
           aes(x = Module,y = Pct_Least,fill = 'Least effective'),
           stat = "identity")+
  geom_text(data = SurveyData_binary2.FullOverall.b, size = 4.12,
            aes(x = Module,y= -0.42,
                label=scales::percent(abs(round(Pct_Least,2)))))+
  scale_x_discrete(limits=rev)+
  coord_flip()+
  geom_hline(yintercept=0, color = "black", size=.2)+
  labs(x = NULL,y = "Percentage", fill = NULL)+
       #title = "Multi-site meeting effectiveness - All sites")+
  scale_y_continuous(breaks=c(-.4,-.3,-.2,-.1,0,.10,.20,.30),
                     labels=c('40','30','20', '10',
                              '0','10','20','30'))+
  scale_fill_brewer(palette = "Accent", labels=c('Least effective', 'Most effective'),
                    direction = -1)+
  theme_light(base_size = 16)+
  theme(legend.position = "bottom")
#dev.off()
```

```{r eval=FALSE, include=FALSE}
## Sites
SurveyData_binary2.Full.b <- 
  SurveyData_binary2.Full.a %>% 
  group_by(University) %>% 
  summarize(Pct_Most = MostEffective/sum(MostEffective),
            Pct_Least = -1*LeastEffective/sum(LeastEffective))

SurveyData_binary2.FullTmp <- cbind(SurveyData_binary2.Full.a,SurveyData_binary2.Full.b[,2:3])

SurveyData_binary2.Full <-
  SurveyData_binary2.FullTmp %>% 
    filter(!is.na(Module)) %>% 
    select(-c(MostEffective,LeastEffective)) %>% 
    pivot_longer(c(Pct_Most,Pct_Least), names_to = "Response",values_to = "Pct")

#tiff("Figs/Multi-siteMeetings/Multi-siteMeetingsSites.tiff",width = 8.49, height = 5.52, units = "in", res = 300)
ggplot(SurveyData_binary2.Full, aes(Module, Pct, fill = Response))+
  coord_flip()+
  geom_bar(stat = "identity")+
  geom_hline(yintercept=0, color = "white", size=.2)+
  labs(x = NULL,y = NULL, fill = NULL)+
  scale_x_discrete(limits=rev)+
  scale_y_continuous(breaks=c(-1,-.5,0,.5,1), labels=c('100%', '50%', '0%',"50%","100%"))+
  scale_fill_brewer(palette = "Accent", labels=c('Least effective', 'Most effective'),direction = -1)+
  facet_wrap(~University)+
  theme_light()+
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1))
#dev.off()
```


Extra- Might not run!!!
#   Cover crop activity
```{r}
SurveyData_likert3 <- SurveyDataNamed[,c(3,23:29)]
SurveyData_likert3[1:8] <- lapply(SurveyData_likert3[1:8], factor)
SurveyData_likert3[2:8] <- lapply(SurveyData_likert3[2:8], factor,
                                   levels = c("Strongly Disagree","Disagree",
                                              "Unsure","Agree","Strongly Agree"))

names(SurveyData_likert3)[1] <- "University"
SurveyData_likert3 %>% 
  count(University)

# Get the current column names of the data frame
SurveyData_likert3.col_names <- colnames(SurveyData_likert3)

# Remove the string "As a result of taking this course I can" from each column name
SurveyData_likert3.col_names_newTmp <- gsub("Indicate your level of agreement or disagreement with the following statements relating to the cover crop challenge: - ",
                                            "", SurveyData_likert3.col_names)
SurveyData_likert3.col_names_newTmp <- str_to_sentence(SurveyData_likert3.col_names_newTmp)
SurveyData_likert3.col_names_new <- gsub("\\.", "",SurveyData_likert3.col_names_newTmp)

# Replace the original column names with the new names
colnames(SurveyData_likert3) <- SurveyData_likert3.col_names_new
colnames(SurveyData_likert3)[8] <- "As a result of this activity, I can more confidently convert values to different units"

# Ploting
##  Overall
likert3.Overall <- likert(SurveyData_likert3[2:8]) 

tiff("Figs/CoverCropChallenge/challengeOverall.tiff",width = 9, height = 5.84, units = "in", res = 300)
plot(likert3.Overall, ordered = TRUE)+
  labs(title = "As a result of the cover crop challenge...",
       subtitle = "All sites (n = 43)")+
  theme(legend.title = element_blank())
dev.off()

##  Cornell
SurveyData_likert3.Cornell<-SurveyData_likert3 %>% 
  filter(University == "Cornell University")
likert3.Cornell <- likert(SurveyData_likert3.Cornell[2:8]) 

tiff("Figs/CoverCropChallenge/challengeCornell.tiff",width = 9, height = 5.84, units = "in", res = 300)
plot(likert3.Cornell, ordered = TRUE)+
  labs(title = "As a result of the cover crop challenge...",
       subtitle = "Cornell University (n = 8)")+
  theme(legend.title = element_blank())
dev.off()

##  Clemson
SurveyData_likert3.Clemson<-SurveyData_likert3 %>% 
  filter(University == "Clemson University")
likert3.Clemson <- likert(SurveyData_likert3.Clemson[2:8]) 

tiff("Figs/CoverCropChallenge/challengeClemson.tiff",width = 9, height = 5.84, units = "in", res = 300)
plot(likert3.Clemson,ordered = TRUE)+
  labs(title = "As a result of the cover crop challenge...",
       subtitle = "Clemson University (n = 4)")+
  theme(legend.title = element_blank())
dev.off()

##  U_Nebraska
SurveyData_likert3.U_Nebraska<-SurveyData_likert3 %>% 
  filter(University == "University of Nebraska")
likert3.U_Nebraska <- likert(SurveyData_likert3.U_Nebraska[2:8]) 

tiff("Figs/CoverCropChallenge/challengeUNL.tiff",width = 9, height = 5.84, units = "in", res = 300)
plot(likert3.U_Nebraska, ordered = TRUE)+
  labs(title = "As a result of the cover crop challenge...",
       subtitle = "University of Nebraska (n = 8)")+
  theme(legend.title = element_blank())
dev.off()

##  U_Kentucky - work on
SurveyData_likert3.UK<-SurveyData_likert3 %>% 
  filter(University == "University of Kentucky") 
likert3.U_Kentucky <- likert(SurveyData_likert3.UK[2:8]) 

tiff("Figs/CoverCropChallenge/challengeUK.tiff",width = 9, height = 5.84, units = "in", res = 300)
plot(likert3.U_Kentucky,ordered = TRUE)+
  labs(title = "As a result of the cover crop challenge...",
       subtitle = "University of Kentucky (n = 8)")+
  theme(legend.title = element_blank())
dev.off()

##  UNH
SurveyData_likert3.UNH<-SurveyData_likert3 %>% 
  filter(University == "University of New Hampshire")
likert3.UNH <- likert(SurveyData_likert3.UNH[2:8]) 

tiff("Figs/CoverCropChallenge/challengeUNH.tiff",width = 9, height = 5.84, units = "in", res = 300)
plot(likert3.UNH, ordered = TRUE)+
  labs(title = "As a result of the cover crop challenge...",
       subtitle = "University of New Hampshire (n = 3)")+
  theme(legend.title = element_blank())
dev.off()

##  Michigan State
SurveyData_likert3.MSU<-SurveyData_likert3 %>% 
  filter(University == "Michigan State University")
likert3.MSU <- likert(SurveyData_likert3.MSU[2:8]) 

tiff("Figs/CoverCropChallenge/challengeMSU.tiff",width = 9, height = 5.84, units = "in", res = 300)
plot(likert3.MSU, ordered = TRUE)+
  labs(title = "As a result of the cover crop challenge...",
       subtitle = "Michigan State University (n = 12)")+
  theme(legend.title = element_blank())
dev.off()

#Table
SurveyData_likert3_Table<-
  SurveyData_likert3 %>% 
    pivot_longer(2:8,names_to = "Question",values_to = "LikertValue") %>% 
    count(Question, University, LikertValue, .drop = F) %>% 
    mmtable(.,n) + 
        header_top(Question) +
        header_left(LikertValue) + 
        header_left_top(University)
SurveyData_likert3_Table
```

#   Cover crop ratings
```{r}
SurveyData_Growth <- SurveyDataNamed[,c(3,31)]
colnames(SurveyData_Growth)[2] <- "GrowthRating"
colnames(SurveyData_Growth)[1] <- "University"

SurveyData_Growth<-
  SurveyData_Growth %>% 
    mutate(GrowthRating = dplyr::recode(GrowthRating, "1 (poor)" = "1", "5 (excellent)" = "5")) %>% 
    filter(!is.na(GrowthRating))

SurveyData_Growth$GrowthRating <- as.numeric(as.character(SurveyData_Growth$GrowthRating))


tiff("Figs/CoverCropGrowth.tiff",width = 7, height = 5.84, units = "in", res = 300)
ggplot(SurveyData_Growth, aes(x = GrowthRating, y = University)) +
  ggridges::geom_density_ridges(aes(fill = University, alpha = .5)) +
  labs(x = "Cover crop growth rating",y=NULL)+
  scale_y_discrete(limits=rev)+
  expand_limits(y = 8)+
  theme_light(base_size = 14)+
  theme(legend.position = "none")
dev.off()

#Everything - Not going to include
ggplot(SurveyData_Growth, aes(x = GrowthRating)) +
  geom_density(fill = "lightblue", alpha = .75) +
  labs(x = "Cover crop growth rating",y=NULL)+
  theme_light(base_size = 14)+
  theme(legend.position = "none")
```

#Correlations
```{r}
SurveyData_Corr <- SurveyDataNamed[,c(3,23:29,31)]

colnames(SurveyData_Corr)[1] <- "University"
colnames(SurveyData_Corr)[9] <- "GrowthRating"

SurveyData_Corr<-
  SurveyData_Corr %>% 
    mutate(GrowthRating = dplyr::recode(GrowthRating, "1 (poor)" = "1", "5 (excellent)" = "5"))
SurveyData_Corr$GrowthRating <- as.numeric(as.character(SurveyData_Corr$GrowthRating))

SurveyData_Corr[1:8] <- lapply(SurveyData_Corr[1:8], factor)
SurveyData_Corr[2:8] <- lapply(SurveyData_Corr[2:8], factor,
                                   levels = c("Strongly Disagree","Disagree",
                                              "Unsure","Agree","Strongly Agree"),
                                    labels = c(1,2,3,4,5))
SurveyData_Corr[2:8] <- lapply(SurveyData_Corr[2:8], as.numeric)

# Get the current column names of the data frame
SurveyData_Corr.col_names <- colnames(SurveyData_Corr)

# Remove the string "As a result of taking this course I can" from each column name
SurveyData_Corr.col_names_newTmp <- gsub("Indicate your level of agreement or disagreement with the following statements relating to the cover crop challenge: - ",
                                            "", SurveyData_Corr.col_names)
SurveyData_Corr.col_names_newTmp <- str_to_sentence(SurveyData_Corr.col_names_newTmp)
SurveyData_Corr.col_names_new <- gsub("\\.", "",SurveyData_Corr.col_names_newTmp)

# Replace the original column names with the new names
colnames(SurveyData_Corr) <- SurveyData_Corr.col_names_new
library(broom.mixed)

SurveyData_Corr %>% 
  pivot_longer(2:8, names_to = "Question", values_to = "LikertValue") %>% 
  nest_by(Question) %>% 
  mutate(mod = list(lmerTest::lmer(LikertValue ~ Growthrating + (1|University),
                                   data = data))) %>% 
  summarize(Effect = tidy(mod)$estimate, P.value = tidy(mod)$p.value)
```

