---
title: "Cover crop class"
output: html_document
date: "2023-02-06"
---

Notes:
Stephene Perry from Cornell Stats Consulting recommends against additional statistical tests on the Likert scale data (5/22/2023). So the confidence intervals for overall satisfaction and multi-site design are just for fun...

#   Loading
```{r}

library(openxlsx)
library(maps)
library(likert)
library(patchwork)
library(janitor)
library(tidyverse)
library(ggstats)
library(here)

library(ggplot2); theme_set(theme_bw() + 
                            theme(panel.grid = element_line(colour = "grey87"),
                                  panel.grid.major = element_line(linewidth = rel(.95)), 
                                  panel.grid.minor = element_line(linewidth = 0)))

SurveyData_22 <- read.xlsx("data/2022 Data/CoverCropSurvey2022_Cleaned.xlsx", sheet = 1)
SurveyData_23 <- read.xlsx("data/2023 Data/CoverCropSurvey2023_Cleaned.xlsx", sheet = 1)

SurveyData_22$Year <- 2022
SurveyData_23$Year <- 2023

SurveyDataFull_Tmp <- bind_rows(SurveyData_22,SurveyData_23)

#Which are not matches
LogicTmp1 <- 
  SurveyDataFull_Tmp %>% 
    filter(Progress == "Progress") %>% 
    select(Year, everything()) 
LogicTmp2 <- LogicTmp1 %>% summarise_all(~all(. == .[[1]]))

LogicTmp <- rbind(LogicTmp1, LogicTmp2)
LogicTmp[which(LogicTmp[3,]==FALSE)] ## only the "in terms of learning" (2023) versus "favorite" for multi-site meetups. Not an issue for the cover crop challenge analysis!


SurveyDataFull <- SurveyDataFull_Tmp[-45,] #removed headers from 2023 survey, IF THE NUMBER OF RESPONDERS CHANGE, YOU NEED  TO CHANGE THE ROW NUMBER!!!
SurveyDataFull <- SurveyDataFull %>%  select(Year,everything())

unique(SurveyDataFull$Q63)
SurveyDataFull <- SurveyDataFull %>% 
  mutate(region = case_when(
    Q63 == "Cornell University" ~ "new york",
    Q63 == "Clemson University" ~ "south carolina",
    Q63 == "University of Nebraska" ~ "nebraska",
    Q63 == "University of Kentucky" ~ "kentucky",
    Q63 == "University of New Hampshire" ~ "new hampshire",
    Q63 == "Michigan State University" ~ "michigan"))

SurveyDataNamed <- SurveyDataFull
colnames(SurveyDataNamed) <- SurveyDataNamed[1,]
SurveyDataNamed <- SurveyDataNamed[-1,] 
names(SurveyDataNamed)[names(SurveyDataNamed) == "2022"] <- "Year"
```

#   Map of students
```{r}
us_states <- map_data("state")

univ_data <- data.frame(
  university = c("Cornell", "Clemson", "UNL", 
                 "UK", "UNH", "MSU"),
  state = c("New York", "South Carolina", "Nebraska", "Kentucky", "New Hampshire", "Michigan"),
  lon = c(-76.48, -82.83, -96.67, -84.5, -71.54, -84.55),
  lat = c(42.45, 34.67, 40.82, 37.83, 43.2, 43.00))

SurveyDataState <- SurveyDataFull[-1,] %>%
  group_by(Year) %>% 
  count(region) %>% 
  arrange(n) %>% 
  mutate(state = str_to_title(region)) %>% 
  left_join(.,univ_data) %>% 
  mutate(university = paste(university," ","(",n,")",sep = ""))

SurveyDataNamed[,c(1,4)] %>% 
  group_by(Year) %>% 
  count()

us_states <- map_data("state")

Year.labs <- c("2022 (*n* = 43)", "2023 (*n* = 35)")
names(Year.labs) <- c("2022", "2023")

#MapPlot<-
  ggplot(us_states,aes(long, lat)) +
    geom_polygon(aes(group = group), fill = "grey95", color = "black",
                 linewidth = .275)+
    geom_point(data = univ_data, aes(x = lon, y = lat), color = "black", size = 2) +
    ggrepel::geom_label_repel(data = SurveyDataState,
                              aes(x = lon, y = lat, label = university),
                              color = "black",box.padding = .6, label.padding = 0.3,
                              fill = alpha("white",0.85)) +
    coord_fixed(1.3)+
    theme_void()+
    theme(strip.text = ggtext::element_markdown(size = 18, hjust = 0.05))+
    facet_wrap(~Year, nrow = 1,
               labeller = labeller(Year = Year.labs))
#ggsave("outputs/MapPlot.png",MapPlot, width = 7.4, height = 3.3, units = "in", dpi = 600)
#ggsave("outputs/COMP_MapPlot.png",MapPlot, width = 7.4, height = 3.3, units = "in", dpi = 100)
```

#   Overall Satisfaction
```{r}
SurveyData_likert1 <- SurveyDataNamed[,c(1,4:13)]
SurveyData_likert1[1:11] <- lapply(SurveyData_likert1[1:11], factor)
SurveyData_likert1[3:11] <- lapply(SurveyData_likert1[3:11], factor,
                                   levels = c("Strongly Disagree","Disagree",
                                              "Unsure","Agree","Strongly Agree"))

names(SurveyData_likert1)[2] <- "University"
SurveyData_likert1 %>% 
  count()

# Get the current column names of the data frame
SurveyData_likert1.col_names <- colnames(SurveyData_likert1)

# Remove the string "As a result of taking this course I can" from each column name
SurveyData_likert1.col_names_newTmp <- gsub("As a result of taking this course I can ", "",
                                          SurveyData_likert1.col_names)
SurveyData_likert1.col_names_newTmp <- str_to_sentence(SurveyData_likert1.col_names_newTmp)
SurveyData_likert1.col_names_new <- gsub("\\.", "",SurveyData_likert1.col_names_newTmp)

# Replace the original column names with the new names
colnames(SurveyData_likert1) <- SurveyData_likert1.col_names_new

# Plotting
## Overall
likert1.all <- likert(SurveyData_likert1[3:11]) 
#Overall_Rev<-
  plot(likert1.all, text.size=3.5,ordered = TRUE)+
    labs(subtitle = "2022 and 2023 (n = 78)")+
    scale_y_continuous(labels = abs, limits = c(-120, 135))+
    theme(legend.title = element_blank(),
          legend.position = "bottom",
          legend.justification = 1)
#ggsave("outputs/Overall_Rev.png", Overall_Rev, width = 6.55, height = 5.3, units = "in", dpi = 600)

##Setting
SurveyData_likert1 <- 
  SurveyData_likert1 %>% 
  mutate(Setting = case_when(
    University %in% c("University of New Hampshire", "Michigan State University") ~ "Greenhouse (n = 35)",
    University == "Cornell University" & Year == 2023 ~ "Greenhouse (n = 35)",
    .default = "Greenhouse and Field (n = 43)"))

gglikert(SurveyData_likert1, include = colnames(SurveyData_likert1[3:11]),
         exclude_fill_values = "Unsure", sort = "none",
         add_labels = FALSE, totals_fontface = "plain", totals_hjust = 0.2,
         facet_cols = vars(Setting))+
  geom_vline(xintercept = 0, color = "grey40")+
  theme_minimal()+
  scale_x_continuous(labels = function(x) scales::label_percent()(abs(x)), limits = c(-1.20, 1.35))+
  theme(strip.text.x = element_text(size = 12, hjust = 0), 
        legend.position = "bottom")
```


#   Lab effectivness
Split up in terms of year because activities changed slightly (no Townhall, notice the two module 12s)
```{r}
SurveyData_binary1 <- SurveyDataNamed[,c(1,4,19:20)]

FactorNames <- c("Module 1: CropScape and Web Soil Survey",
                 "Module 2: Cover crop challenge: start",
                 "Module 3: Cover crop emergence: seed size x planting depth",
                 "Module 4: Cover crop ground cover: species x planting rate",
                 "Module 5: Online mixture calculators",
                 "Module 7: Soil health activities and exercises",
                 "Module 8: Cover crop challenge: harvest and multifunctionality",
                 "Module 9: Cover crop challenge: weighing samples",
                 "Module 10: Cover crop innovations: introduction",
                 "Module 11: Cover crop partial budgets",
                 "Module 12: Town hall preparation",
                 "Module 12: Cover crop adoption discussion",
                 "Module 13: Cover crop innovations: presentations")


unique(na.omit(SurveyData_binary1[,3])) %in% FactorNames #NA not present but that's okay
unique(na.omit(SurveyData_binary1[,4])) %in% FactorNames #NA not present but that's okay

SurveyData_binary1[1:4] <- lapply(SurveyData_binary1[1:4], factor)
SurveyData_binary1[3:4] <- lapply(SurveyData_binary1[3:4], factor,
                                   levels = c("Module 1: CropScape and Web Soil Survey",
                                              "Module 2: Cover crop challenge: start",
                                              "Module 3: Cover crop emergence: seed size x planting depth",
                                              "Module 4: Cover crop ground cover: species x planting rate",
                                              "Module 5: Online mixture calculators",
                                              "Module 7: Soil health activities and exercises",
                                              "Module 8: Cover crop challenge: harvest and multifunctionality",
                                              "Module 9: Cover crop challenge: weighing samples",
                                              "Module 10: Cover crop innovations: introduction",
                                              "Module 11: Cover crop partial budgets",
                                              "Module 12: Town hall preparation",
                                              "Module 12: Cover crop adoption discussion",
                                              "Module 13: Cover crop innovations: presentations"),
                                  labels = c("Module 1: CropScape and Web Soil Survey",
                                              "Module 2: Cover crop challenge: Start",
                                              "Module 3: Cover crop emergence: Seed size x planting depth",
                                              "Module 4: Cover crop ground cover: Species x planting rate",
                                              "Module 5: Online mixture calculators",
                                              "Module 7: Soil health activities and exercises",
                                              "Module 8: Cover crop challenge: Harvest and multifunctionality",
                                              "Module 9: Cover crop challenge: Weighing samples",
                                              "Module 10: Cover crop innovations: Introduction",
                                              "Module 11: Cover crop partial budgets",
                                              "Module 12: Town hall preparation",
                                              "Module 12: Cover crop adoption discussion",
                                              "Module 13: Cover crop innovations: Presentations"))

names(SurveyData_binary1)[2] <- "University"
names(SurveyData_binary1)[3] <- "MostEffective"
names(SurveyData_binary1)[4] <- "LeastEffective"

#Plotting----
#In 2022 we didn't have the Cover crop adoption discussion, in 2023 we didn't have the Town hall preparation
SurveyData_binary1.FullOverall.a<-
  SurveyData_binary1 %>% 
    group_by(Year) %>% 
    count(MostEffective,.drop = FALSE) %>% 
    drop_na(MostEffective) %>% 
    rename(Module = MostEffective, MostEffective = n) %>% 
    filter(Year == 2022 & !Module == "Module 12: Cover crop adoption discussion" |
           Year == 2023 & !Module == "Module 12: Town hall preparation") %>% 
    mutate(Pct_Most = MostEffective/sum(MostEffective))

SurveyData_binary1.FullOverall.b<-
  SurveyData_binary1 %>% 
    group_by(Year) %>% 
    count(LeastEffective,.drop = FALSE) %>% 
    drop_na(LeastEffective) %>% 
    rename(Module = LeastEffective, LeastEffective = n) %>% 
    filter(Year == 2022 & !Module == "Module 12: Cover crop adoption discussion" |
           Year == 2023 & !Module == "Module 12: Town hall preparation") %>% 
    mutate(Pct_Least = -1*LeastEffective/sum(LeastEffective))

SurveyData_binary1.FullOverallTmp <- full_join(SurveyData_binary1.FullOverall.a,
                                               SurveyData_binary1.FullOverall.b)

SurveyData_binary1.FullOverall <-
  SurveyData_binary1.FullOverallTmp %>% 
    select(-c(MostEffective,LeastEffective)) %>% 
    pivot_longer(c(Pct_Most,Pct_Least), names_to = "Response",values_to = "Pct") %>% 
    mutate(Year.Mod = paste(Year,Module,sep = "."))

#LabValues created to order values in the plot
LabValues <- SurveyData_binary1.FullOverall %>% 
  group_by(Year,Module) %>% 
  summarise(Pct_Most = sum(Pct[Pct > 0],na.rm = TRUE)*100,
            Pct_Least = sum(Pct[Pct < 0],na.rm = TRUE)*100) %>% 
  mutate(Year.Mod = paste(Year,Module,sep = ".")) %>% 
  arrange(Year,Pct_Most,Pct_Least)

SurveyData_binary1.FullOverall$Year.Mod <-
  factor(SurveyData_binary1.FullOverall$Year.Mod,
         levels = LabValues$Year.Mod)
#LabPlot <-
  SurveyData_binary1.FullOverall %>% 
    mutate(Pct = Pct*100) %>% 
  ggplot(., aes(Year.Mod,Pct,fill=Response))+
    coord_flip()+
    geom_bar(stat = "identity")+
    geom_text(aes(x = Year.Mod,y= if_else(Response == "Pct_Least",-42,42),
                  label=paste(abs(round(Pct,0)),"%")))+
    geom_hline(yintercept=0, color = "black", linewidth=.2)+
    labs(x = NULL,y = "Percentage", fill = NULL)+
    scale_x_discrete(labels = function(x) gsub(".*?(\\d+:)", "", x))+
    scale_fill_discrete(labels = c("Least effective", "Most effective"))+
    ylim(-50,50)+
    theme(legend.position = "bottom")+
    facet_wrap(~Year, nrow = 2, scales = "free_y")
#ggsave("outputs/LabPlot.svg",LabPlot,width = 5.12, height = 5.95, units = "in", dpi = 600)

#Table----
#How is CCC capitalized?
unique(SurveyData_binary1$MostEffective) #Cover crop challenge
unique(SurveyData_binary1$LeastEffective) #Cover crop challenge

SurveyData_binary1_Tab1 <- data.frame(table(SurveyData_binary1$MostEffective,SurveyData_binary1$Year))
#In 2022 we didn't have the Cover crop adoption discussion, in 2023 we didn't have the Town hall preparation
SurveyData_binary1_Tab1 <- SurveyData_binary1_Tab1 %>% 
    filter(Var2 == 2022 & !Var1 == "Module 12: Cover crop adoption discussion" |
           Var2 == 2023 & !Var1 == "Module 12: Town hall preparation")


SurveyData_binary1_Tab2 <-
  SurveyData_binary1_Tab1 %>% 
    group_by(Var2) %>% 
    mutate(n_year = sum(Freq),
           Prop = Freq/n_year*100) %>% 
    rename(Module = Var1, Year = Var2) %>% 
    mutate(Module = gsub(".*?(\\d+:) ", "", Module)) %>% 
    select(Year,Module,everything()) %>% 
    ungroup()

SurveyData_binary1_Tab2 %>% 
  mutate(CCC = 
           case_when(str_detect(Module, "Cover crop challenge") == 
                       TRUE ~ as.character("Cover crop challenge"),
                     .default = as.character("Not CCC"))) %>% 
  group_by(Year,CCC) %>% 
  summarise(MeanEff = mean(Prop))

LabTab<-
  SurveyData_binary1_Tab2 %>% 
    mutate(CCC = 
             case_when(str_detect(Module, "Cover crop challenge") == 
                         TRUE ~ as.character(Module),
                       .default = as.character("Not CCC"))) %>% 
    group_by(Year,CCC) %>% 
    summarise(MeanEff = round(mean(Prop),0))

#write.xlsx(LabTab, "LabTab.xlsx")
```


#   Multi-site activity
- Years split because question format was slightly different and three of the activities were different
```{r}
SurveyData_binary2 <- SurveyDataNamed[,c(1,4,21:22)]
SurveyData_binary2[1:4] <- lapply(SurveyData_binary2[1:4], factor)

names(SurveyData_binary2)[2] <- "University"
names(SurveyData_binary2)[3] <- "MostEffective"
names(SurveyData_binary2)[4] <- "LeastEffective"  

Binary2Levels <-
  as_tibble(as.character(unique(c(SurveyData_binary2$MostEffective,SurveyData_binary2$LeastEffective)))) %>% 
    na.omit() %>% 
    arrange(as.numeric(str_extract(value, "^\\d+")))

Binary2Labels <-
  Binary2Levels %>% 
  mutate(value = str_remove(value, ".*\\.\\s"))

SurveyData_binary2[3:4] <- lapply(SurveyData_binary2[3:4], factor,
                                  levels = Binary2Levels$value,
                                  labels = Binary2Labels$value)

#Plotting----
#In 2022 we didn't have "Farmer panel on nutrient cycling" (8), "Cover crop adoption panel" (11), or "Student innovator presentations" (12)
#In 2023 we didn't have the "Cover crops and soil N" (8), "Town hall role-playing" (11), or "Innovator presentations" (12)
SurveyData_binary2.FullOverall.a <-
  SurveyData_binary2 %>% 
    group_by(Year) %>% 
    count(MostEffective,.drop = FALSE) %>% 
    drop_na(MostEffective) %>% 
    rename(Module = MostEffective, MostEffective = n) %>% 
    filter(Year == 2022 & !Module == "Farmer panel on nutrient cycling" & !Module == "Cover crop adoption panel" & !Module == "Student innovator presentations"|
           Year == 2023 & !Module == "Cover crops and soil N" & !Module == "Town hall role-playing" & !Module == "Innovator presentations") %>%   
    mutate(Pct_Most = MostEffective/sum(MostEffective),
           YearTotal = sum(MostEffective))

SurveyData_binary2.FullOverall.b <-
  SurveyData_binary2 %>% 
    group_by(Year) %>% 
    count(LeastEffective,.drop = FALSE) %>% 
    drop_na(LeastEffective) %>% 
    rename(Module = LeastEffective, LeastEffective = n) %>% 
    filter(Year == 2022 & !Module == "Farmer panel on nutrient cycling" & !Module == "Cover crop adoption panel" & !Module == "Student innovator presentations"|
           Year == 2023 & !Module == "Cover crops and soil N" & !Module == "Town hall role-playing" & !Module == "Innovator presentations") %>%   
    mutate(Pct_Least = -1*LeastEffective/sum(LeastEffective),
           YearTotal = sum(LeastEffective))

SurveyData_binary2.FullOverallTmp <- full_join(SurveyData_binary2.FullOverall.a,
                                               SurveyData_binary2.FullOverall.b,
                                               by = c("Year", "Module"))

SurveyData_binary2.FullOverall <-
  SurveyData_binary2.FullOverallTmp %>% 
    select(-c(MostEffective,LeastEffective)) %>% 
    pivot_longer(c(Pct_Most,Pct_Least), names_to = "Response",values_to = "Pct") %>% 
    mutate(Year.Mod = paste(Year,Module,sep = "."))

#LabValues created to order values in the plot
LabValues_Multi <- SurveyData_binary2.FullOverall %>% 
  group_by(Year,Module) %>% 
  summarise(Pct_Most = sum(Pct[Pct > 0],na.rm = TRUE)*100,
            Pct_Least = sum(Pct[Pct < 0],na.rm = TRUE)*100) %>% 
  mutate(Year.Mod = paste(Year,Module,sep = ".")) %>% 
  arrange(Year,Pct_Most,Pct_Least)

SurveyData_binary2.FullOverall$Year.Mod <-
  factor(SurveyData_binary2.FullOverall$Year.Mod,
         levels = LabValues_Multi$Year.Mod)

# Function to remove period AND capitalize after colon. Done to match figure from lab.
capitalize_after_colon <- function(x) {
  x <- gsub(".*?\\.", "", x)
  x <- gsub("(?<=:)(\\s*[a-z])", "\\U\\1", x, perl = TRUE)
  return(x)
}

SurveyData_binary2.FullOverall %>% 
  mutate(Pct = Pct*100,
         Year.Mod = fct_recode(Year.Mod,
                               "2022.Cover crop challenge: results" = "2022.cover crop challenge results",
                               "2023.Cover crop challenge: results" = "2023.cover crop challenge results")) %>% 
ggplot(., aes(Year.Mod,Pct,fill=Response))+
  coord_flip()+
  geom_bar(stat = "identity")+
  geom_text(aes(x = Year.Mod,y= if_else(Response == "Pct_Least",-52,42),
                label=paste(abs(round(Pct,0)),"%")))+
  geom_hline(yintercept=0, color = "black", linewidth=.2)+
  labs(x = NULL,y = "Percentage", fill = NULL)+
  scale_x_discrete(labels = capitalize_after_colon)+
  scale_fill_discrete(labels = c("Least effective", "Most effective"))+
  ylim(-60,50)+
  theme(legend.position = "bottom")+
  facet_wrap(~Year, nrow = 2, scales = "free_y")

#Table----
#How is CCC capitalized?
unique(SurveyData_binary2$MostEffective) #cover crop challenge
unique(SurveyData_binary2$LeastEffective) #cover crop challenge

SurveyData_binary2_Tab1 <- data.frame(table(SurveyData_binary2$MostEffective,SurveyData_binary2$Year))

#In 2022 we didn't have "Farmer panel on nutrient cycling" (8), "Cover crop adoption panel" (11), or "Student innovator presentations" (12)
#In 2023 we didn't have the "Cover crops and soil N" (8), "Town hall role-playing" (11), or "Innovator presentations" (12)
SurveyData_binary2_Tab1 <- SurveyData_binary2_Tab1 %>% 
 filter(Var2 == 2022 & !Var1 == "Farmer panel on nutrient cycling" & !Var1 == "Cover crop adoption panel" & !Var1 == "Student innovator presentations"|
           Var2 == 2023 & !Var1 == "Cover crops and soil N" & !Var1 == "Town hall role-playing" & !Var1 == "Innovator presentations")

SurveyData_binary2_Tab2 <-
  SurveyData_binary2_Tab1 %>% 
    group_by(Var2) %>% 
    mutate(n_year = sum(Freq),
           Prop = Freq/n_year*100) %>% 
    rename(Module = Var1, Year = Var2) %>% 
    mutate(Module = gsub(".*?(\\d+:) ", "", Module)) %>% 
    select(Year,Module,everything()) %>% 
    ungroup()

SurveyData_binary2_Tab2 %>% 
  mutate(CCC = 
           case_when(str_detect(Module, "cover crop challenge") == 
                       TRUE ~ as.character("cover crop challenge"),
                     .default = as.character("Not CCC"))) %>% 
  group_by(Year,CCC) %>% 
  summarise(MeanEff = mean(Prop))

ActTab<-
  SurveyData_binary2_Tab2 %>% 
    mutate(CCC = 
             case_when(str_detect(Module, "cover crop challenge") == 
                         TRUE ~ as.character(Module),
                       .default = as.character("Not CCC"))) %>% 
    group_by(Year,CCC) %>% 
    summarise(MeanEff = round(mean(Prop),0))
#write.xlsx(ActTab,"ActTab.xlsx")
```

#   Cover crop activity
```{r}
SurveyData_likert3 <- SurveyDataNamed[,c(1,4,24:30)]
SurveyData_likert3[1:9] <- lapply(SurveyData_likert3[1:9], factor)
SurveyData_likert3[3:9] <- lapply(SurveyData_likert3[3:9], factor,
                                   levels = c("Strongly Disagree","Disagree",
                                              "Unsure","Agree","Strongly Agree"))

names(SurveyData_likert3)[2] <- "University"
SurveyData_likert3 %>% 
  count(Year)

# Get the current column names of the data frame
SurveyData_likert3.col_names <- colnames(SurveyData_likert3)

# Remove the string "As a result of taking this course I can" from each column name
SurveyData_likert3.col_names_newTmp <- gsub("Indicate your level of agreement or disagreement with the following statements relating to the cover crop challenge: - ",
                                            "", SurveyData_likert3.col_names)
SurveyData_likert3.col_names_newTmp <- str_to_sentence(SurveyData_likert3.col_names_newTmp) #Sentence case
SurveyData_likert3.col_names_newTmp <- gsub("\\.", "",SurveyData_likert3.col_names_newTmp) #Remove periods
SurveyData_likert3.col_names_newTmp <- str_replace_all(SurveyData_likert3.col_names_newTmp,"excel","Excel") #uppercase Excel
SurveyData_likert3.col_names_new <- str_replace_all(SurveyData_likert3.col_names_newTmp,"cover crop challenge","Cover Crop Challenge") #uppercase CCC

# Replace the original column names with the new names
colnames(SurveyData_likert3) <- SurveyData_likert3.col_names_new
colnames(SurveyData_likert3)[9] <- "As a result of this activity, I can more confidently convert values to different units" #capitalizing the "I"

# Ploting
##  Overall
likert3.Overall <- likert(SurveyData_likert3[3:9]) 
#CCC_Rev<-
  plot(likert3.Overall, text.size=3.5,group.order = colnames(SurveyData_likert3)[3:9])+
    labs(subtitle = expression(paste("2022 and 2023 (",italic(n), " = 78)")))+
    scale_y_continuous(labels = abs, limits = c(-115, 120))+
    theme(legend.title = element_blank(),
          legend.position = "bottom",
          legend.justification = 1)

#ggsave("outputs/CCC_Rev.png", CCC_Rev, width = 6.55, height = 5, units = "in", dpi = 600)

##Split
SurveyData_likert3 <- 
  SurveyData_likert3 %>% 
  mutate(Setting = case_when(
    University %in% c("University of New Hampshire", "Michigan State University") ~ "Field-only (*n* = 35)",
    University == "Cornell University" & Year == 2023 ~ "Field-only (*n* = 35)",
    .default = "Greenhouse and field (*n* = 43)")) %>% 
  select(1:7,9,8,everything()) #just reodering

CCC_Rev_split <-  
  gglikert(SurveyData_likert3, include = colnames(SurveyData_likert3[3:9]),
           exclude_fill_values = "Unsure",
           sort = "none",
           add_labels = FALSE, totals_fontface = "plain", totals_hjust = 0.2,
           facet_cols = vars(Setting))+
  geom_vline(xintercept = 0, color = "grey40")+
  scale_x_continuous(labels = function(x) scales::label_percent()(abs(x)), limits = c(-1.20, 1.35))+
  scale_fill_likert(labels = c("Strongly disagree","Disagree","Agree","Strongly agree"))+
  theme_minimal()+
  theme(strip.text.x = ggtext::element_markdown(size = 12, hjust = 0),
        legend.position = "bottom",
        panel.border = element_rect(color = "black", fill = NA, size = .5))
#ggsave("outputs/CCC_Rev_Split.png", CCC_Rev_split, width = 8.35, height = 4.45, units = "in", dpi = 600)

##Years
SurveyData_likert3.22<-SurveyData_likert3 %>% 
  filter(Year == "2022")
likert3.22 <- likert(SurveyData_likert3.22[3:9]) 

likert3.22Plot <-
  plot(likert3.22, group.order = colnames(SurveyData_likert3.22)[3:9])+
    labs(subtitle = "2022 (n = 43)")+
    scale_y_continuous(labels = abs, limits = c(-120, 135))+
    theme(legend.title = element_blank(),
          legend.position = "bottom")

SurveyData_likert3.23<-SurveyData_likert3 %>% 
  filter(Year == "2023")
likert3.23 <- likert(SurveyData_likert3.23[3:9]) 

likert3.23Plot <-
  plot(likert3.23, group.order = colnames(SurveyData_likert3.23)[3:9])+
    labs(subtitle = "2023 (n = 35)")+
    scale_y_continuous(labels = abs, limits = c(-120, 135))+
    theme(legend.title = element_blank(),
          legend.position = "bottom")

likert3.Leg <- ggpubr::get_legend(plot(likert3.23)+
                                    theme(legend.title = element_blank()))
likert3.Leg <- ggpubr::as_ggplot(likert3.Leg)

likert3_patch1<-likert3.22Plot/likert3.23Plot+
  plot_layout(guides = "collect", axes = "collect") &
  theme(legend.position = "none")

likert3_patch2 <- likert3.Leg+plot_spacer()+
    plot_layout(widths = c(0,8005))

#547 x 698
likert3_patch1/plot_spacer()/likert3_patch2+
  plot_layout(nrow = 4,heights = c(1,1,0,.07))

#Table
#SurveyData_likert3_Table<-
 # SurveyData_likert3 %>% 
  #  pivot_longer(2:8,names_to = "Question",values_to = "LikertValue") %>% 
   # count(Question, University, LikertValue, .drop = F) %>% 
    #mmtable2::mmtable(.,n) + 
     #   header_top(Question) +
      #  header_left(LikertValue) + 
       # header_left_top(University)
#SurveyData_likert3_Table

###Natasha
ValueSpread <-
  SurveyData_likert3 %>% 
  select(Year, University, 3) %>% 
  drop_na() %>% 
  mutate(Manditory = case_when(University == "Cornell University"|
                          University == "University of New Hampshire" & Year == 2023 ~ "Yes",
                          .default = "No"))

ggplot(ValueSpread, aes(Manditory, `The Cover Crop Challenge was a valuable activity`))+
  coord_flip()+
  geom_jitter(width = 0.10, height = 0.12)+
  labs(title=(expression(paste("Was the survey ",bold("manditory"), "?"))),
       subtitle = "Students that were not forced to take the survey could be bias to\nonly respond if they felt strongly about the cover crop challenge")+
  theme(axis.title.y = element_blank(),
        plot.subtitle = element_text(size = rel(.9)))
```

#   Cover crop ratings
```{r}
SurveyData_Growth <- SurveyDataNamed[,c(1,4,32)]
colnames(SurveyData_Growth)[3] <- "GrowthRating"
colnames(SurveyData_Growth)[2] <- "University"

SurveyData_Growth<-
  SurveyData_Growth %>% 
    mutate(GrowthRating = dplyr::recode(GrowthRating, "1 (poor)" = "1", "5 (excellent)" = "5")) %>% 
    filter(!is.na(GrowthRating))

SurveyData_Growth$GrowthRating <- as.numeric(as.character(SurveyData_Growth$GrowthRating))

ggplot(SurveyData_Growth, aes(x = GrowthRating, y = University)) +
  ggridges::geom_density_ridges(aes(fill = University, alpha = .5)) +
  labs(x = "Cover crop growth rating",y=NULL)+
  scale_x_continuous(breaks = c(1,2,3,4,5), labels = c("1\n(poor)",2,3,4,"5\n(excellent)"))+
  scale_y_discrete(limits=rev)+
  viridis::scale_fill_viridis(discrete = TRUE, begin = .1, end = .9)+
  expand_limits(y = 8)+
  theme(legend.position = "none")+
  facet_wrap(~Year)

  ggplot(SurveyData_Growth, aes(x = GrowthRating, fill = TRUE,color = NA)) +
    geom_density(aes(alpha = 0.5),color = NA)+
    labs(x = "Student cover crop growth rating", y="Density")+
    scale_x_continuous(breaks = c(1,2,3,4,5), labels = c("1\n(poor)",2,3,4,"5\n(excellent)"))+
    scale_fill_manual(values = "#6165A0")+
    theme(legend.position = "none",
          axis.title.y = element_text(angle = 0,vjust = .5),
          plot.margin = unit(c(5.5, 12.5, 5.5, 5.5), "points"))

RatingsDens <-
  ggplot(SurveyData_Growth, aes(x = GrowthRating))+
    geom_histogram(aes(y = stat(count / sum(count))),
                   alpha = 0.65, color = "black",binwidth = 1)+
    scale_y_continuous(labels = scales::percent_format())+
    labs(x = "Student cover crop growth rating", y="Proportion\nof responses")+
    scale_x_continuous(breaks = c(1,2,3,4,5), labels = c("1\n(poor)",2,3,4,"5\n(excellent)"))+
    theme(axis.title.y = element_text(angle = 0,vjust = .5, hjust = 0),
          plot.margin = unit(c(5.5, 12.5, 5.5, 5.5), "points"))

SurveyData_Growth_sep <-
  SurveyData_Growth %>% 
  mutate(Setting = case_when(
    University %in% c("University of New Hampshire", "Michigan State University") ~ "Field-only (*n* = 35)",
    University == "Cornell University" & Year == 2023 ~ "Field-only (*n* = 35)",
    .default = "Greenhouse and field (*n* = 43)"))

RatingsDens_sep <-
  ggplot(SurveyData_Growth_sep, aes(x = GrowthRating))+
    geom_histogram(aes(y = stat(count / sum(count))),
                   alpha = 0.65, color = "black",binwidth = 1)+
    scale_y_continuous(labels = scales::percent_format())+
    labs(x = "Student cover crop growth rating", y="Proportion\nof responses")+
    scale_x_continuous(breaks = c(1,2,3,4,5), labels = c("1\n(poor)",2,3,4,"5\n(excellent)"))+
    facet_wrap(~Setting)+
    theme_minimal()+
    theme(axis.title.y = element_text(angle = 0,vjust = .5, hjust = 0),
          panel.spacing = unit(1, "lines"),
          strip.text.x = ggtext::element_markdown(size = 11, hjust = 0),
          panel.border = element_rect(color = "black", fill = NA, size = .5))
```

#Correlations
```{r set up}
SurveyData_Corr <- SurveyDataNamed[,c(1,4:13,24:30,32)] #taking from overall, cov. crop challenge, and ratings

#Modifying column names
colnames(SurveyData_Corr)[2] <- "University"

SurveyData_Corr.col_names <- colnames(SurveyData_Corr)

SurveyData_Corr.col_names.new <- gsub("As a result of taking this course I can ", "",
                                      SurveyData_Corr.col_names)
SurveyData_Corr.col_names.new <- gsub("Indicate your level of agreement or disagreement with the following statements relating to the cover crop challenge: - ","",SurveyData_Corr.col_names.new)
SurveyData_Corr.col_names.new <- str_to_sentence(SurveyData_Corr.col_names.new)
SurveyData_Corr.col_names.new <- gsub("i(?=\\s|\\.|$)", "I", SurveyData_Corr.col_names.new, perl = TRUE)
SurveyData_Corr.col_names.new <- gsub("\\.", "",SurveyData_Corr.col_names.new)
colnames(SurveyData_Corr) <- SurveyData_Corr.col_names.new

colnames(SurveyData_Corr)[19] <- "GrowthRating"

#Modifying column types
SurveyData_Corr[1:18] <- lapply(SurveyData_Corr[1:18], factor)
SurveyData_Corr[3:18] <- lapply(SurveyData_Corr[3:18], factor,
                                   levels = c("Strongly Disagree","Disagree",
                                              "Unsure","Agree","Strongly Agree"))
SurveyData_Corr<-
  SurveyData_Corr %>% 
    mutate(GrowthRating = dplyr::recode(GrowthRating, "1 (poor)" = "1", "5 (excellent)" = "5"))
SurveyData_Corr$GrowthRating <- as.numeric(as.character(SurveyData_Corr$GrowthRating))

str(SurveyData_Corr) #looks good!

SurveyData_Corr2 <-SurveyData_Corr

SurveyData_Corr2[3:18] <- lapply(SurveyData_Corr2[3:18], as.numeric) #Numeric worked because of factor leveling, 5 is "Strongly agree" and 1 is "Strongly disagree" - confirmed March 6, 2024

#Rename columns to NOT have special charterers
SurveyData_Corr2 <- 
  SurveyData_Corr2 %>% 
  rename("Discuss the potential long term benefits of cover crops" = "Discuss the potential long-term benefits of cover crops",
         "Explain how cover crop management influences agronomic and environmental outcomes"  = "Explain how cover crop management (eg, seeding time and termination method) influences agronomic and environmental outcomes",
         "I have increased knowledge of how environmental conditions affect performance of individual species in a mixture" = "I have increased knowledge of how environmental conditions (temperature and moisture) affect performance of individual species in a mixture")
```

```{r overall}
library(ggpubr)

#Assumptions----
NorTestFun <- function(z) {
  TestVal <- shapiro.test(SurveyData_Corr2[,z])$p.value
  data.frame(Question = colnames(SurveyData_Corr2)[z], shapiro.test.value = TestVal,
             row.names = NULL)}

shapiro.test.results <- sapply(c(12,3:9),NorTestFun,simplify = FALSE)
shapiro.test.result_df <- do.call(rbind, shapiro.test.results)

#Significance show that I don't have normally distributed data and should use a kendall's correlation
shapiro.test.result_df %>% 
  mutate(Sig = if_else(shapiro.test.value < 0.05, "*",""))

qqplotFun <- function(z) {ggqqplot(SurveyData_Corr2[,z])}
sapply(c(12,3:9),function(z) {ggqqplot(SurveyData_Corr2[,z])})
qqplotFun(12)

#Plot----
CorrPlotFun <- function(z){
  ggscatter(SurveyData_Corr2, x = colnames(SurveyData_Corr2)[12], y = colnames(SurveyData_Corr2)[z],
            add = "reg.line", conf.int = TRUE,
            cor.coef = TRUE, cor.method = "kendall",
            ggtheme = theme_get())+
      geom_jitter(size = .75,width = 0.05, height = .05)+
      scale_x_continuous(breaks = c(1,2,3,4,5))+
      scale_y_continuous(breaks = c(1,2,3,4,5))+
      labs(x = str_wrap(colnames(SurveyData_Corr2)[12], width = 30),
           y = str_wrap(colnames(SurveyData_Corr2)[z], width = 25))+
      theme(axis.title.x = element_blank(),
            axis.title.y = element_text(hjust = 0))
}

CorrPlotFun2 <- function(z){
  ggscatter(SurveyData_Corr2, x = colnames(SurveyData_Corr2)[12], y = colnames(SurveyData_Corr2)[z],
            add = "reg.line", conf.int = TRUE, 
            cor.coef = TRUE, cor.method = "kendall",
            ggtheme = theme_get())+
      geom_jitter(size = .75,width = 0.05, height = .05)+
      scale_x_continuous(breaks = c(1,2,3,4,5))+
      scale_y_continuous(breaks = c(1,2,3,4,5))+
      labs(x = str_wrap(colnames(SurveyData_Corr2)[12], width = 25),
           y = str_wrap(colnames(SurveyData_Corr2)[z], width = 25))+
      theme(axis.title.x = element_text(hjust = 0),
            axis.title.y = element_text(hjust = 0))}

CorrPlotFun(3) + CorrPlotFun(4) + CorrPlotFun(5)+
CorrPlotFun(6) + CorrPlotFun(7) + CorrPlotFun(8)+
CorrPlotFun2(9) + CorrPlotFun2(10) + CorrPlotFun2(11)+
  plot_layout(nrow = 3)


#Class outcomes----
ggscatter(SurveyData_Corr2, x = colnames(SurveyData_Corr2)[12], y = colnames(SurveyData_Corr2)[6],
            add = "reg.line", conf.int = TRUE, cor.method = "kendall",
            ggtheme = theme_get())+
      stat_cor(method = "kendall",cor.coef.name = "tau[b]",label.y.npc = .85)+
      geom_jitter(size = .75,width = 0.08, height = .07)+
      scale_x_continuous(breaks = c(1,2,3,4,5))+
      scale_y_continuous(breaks = c(1,2,3,4,5))+
      labs(x = str_wrap(colnames(SurveyData_Corr2)[12], width = 40),
           y = str_wrap(colnames(SurveyData_Corr2)[6], width = 20))+
      theme(axis.title.y = element_text(angle = 0,vjust = .5,hjust = 0))

#Table----
CorrTableFun <- function(z){
  p_tmp <- cor.test(SurveyData_Corr2[,12], SurveyData_Corr2[,z],
                    method = "kendall", alternative = "two.sided")$p.value
  r_tmp <- cor.test(SurveyData_Corr2[,12], SurveyData_Corr2[,z],
                    method = "kendall", alternative = "two.sided")$estimate
  data.frame(Outcome = colnames(SurveyData_Corr2)[z], correlation = r_tmp, p.value = p_tmp,
             row.names = NULL)}

results <- sapply(3:11,CorrTableFun,simplify = FALSE)
result_df <- do.call(rbind, results)
#write.xlsx(result_df, "corrRes.xlsx")
```

```{r CCC}
colnames(SurveyDataNamed[24:30])
colnames(SurveyData_Corr2)

CorrPlotFun(13) + CorrPlotFun(14) + CorrPlotFun(15) +
CorrPlotFun2(16) + CorrPlotFun2(17) + CorrPlotFun2(18)+
  plot_layout(nrow = 2)

results2 <- sapply(13:18,CorrTableFun,simplify = FALSE)
result2_df <- do.call(rbind, results2)
#write.xlsx(result2_df, "corrRes2.xlsx")

#CCC outcomes----
ggscatter(SurveyData_Corr2, y = colnames(SurveyData_Corr2)[12], x = colnames(SurveyData_Corr2)[13],
            add = "reg.line", conf.int = TRUE, cor.method = "kendall",
            ggtheme = theme_get())+
      stat_cor(method = "kendall",cor.coef.name = "tau[b]",label.y.npc = .925)+
      geom_jitter(size = .75,width = 0.08, height = .07)+
      scale_x_continuous(breaks = c(1,2,3,4,5))+
      scale_y_continuous(breaks = c(1,2,3,4,5))+
      labs(y = str_wrap(colnames(SurveyData_Corr2)[12], width = 20),
           x = str_wrap(colnames(SurveyData_Corr2)[13], width = 40))+
      theme(axis.title.y = element_text(angle = 0,vjust = .5,hjust = 0))

#Rating----
#Check name
colnames(SurveyData_Corr2)[12] #y= "The cover crop challenge was a valuable activity" 
colnames(SurveyData_Corr2)[19] #x = "GrowthRating"

RatingCor <-
  ggscatter(SurveyData_Corr2, y = colnames(SurveyData_Corr2)[12], x = colnames(SurveyData_Corr2)[19],
              add = "reg.line", conf.int = TRUE,cor.method = "kendall",
              ggtheme = theme_get())+
        stat_cor(method = "kendall",cor.coef.name = "tau[b]",label.y.npc = .925)+
        geom_jitter(size = .75,width = 0.08, height = .07)+
        scale_x_continuous(breaks = c(1,2,3,4,5),labels = c("1\n(poor)",2,3,4,"5\n(excellent)"))+
        scale_y_continuous(breaks = c(1,2,3,4,5))+
        labs(y = str_wrap("The Cover Crop Challenge was a valuable activity", width = 20),
             x = "Student cover crop growth rating")+
        theme(axis.title.y = element_text(angle = 0,vjust = .5,hjust = 0),
               plot.margin = unit(c(5.5, 12.5, 5.5, 5.5), "points"))

RatingPatch <- 
  RatingCor + RatingsDens +
    plot_annotation(tag_levels = list(c("a.","b."))) &
    theme(plot.tag.position =  "topleft",
          plot.tag = element_text(size = rel(1.65)))
#ggsave("outputs/RatingPlot.png", RatingPatch, width = 7.265, height = 2.8, units = "in", dpi = 600)

SurveyData_Corr2_split  <- 
  SurveyData_Corr2 %>% 
  mutate(Setting = case_when(
    University %in% c("University of New Hampshire", "Michigan State University") ~ "Field-only (*n* = 35)",
    University == "Cornell University" & Year == 2023 ~ "Field-only (*n* = 35)",
    .default = "Greenhouse and field (*n* = 43)"))

RatingCor_split <-
  ggscatter(SurveyData_Corr2_split, y = colnames(SurveyData_Corr2)[12], x = colnames(SurveyData_Corr2)[19],
              add = "reg.line", conf.int = TRUE,cor.method = "kendall",
              add.params = list(fill = "#B0B0B0"), # Customize reg. line
              ggtheme = theme_get())+
        stat_cor(method = "kendall",cor.coef.name = "tau[b]",label.y.npc = .925)+
        geom_jitter(size = .75,width = 0.08, height = .07)+
        scale_x_continuous(breaks = c(1,2,3,4,5),labels = c("1\n(poor)",2,3,4,"5\n(excellent)"))+
        scale_y_continuous(breaks = c(1,2,3,4,5))+
        labs(y = str_wrap("The Cover Crop Challenge was a valuable activity", width = 20),
             x = "Student cover crop growth rating")+
        facet_wrap(~Setting)+
        theme_minimal()+
        theme(axis.title.y = element_text(angle = 0,vjust = .5,hjust = 0),
              panel.spacing = unit(1, "lines"),
              strip.text.x = ggtext::element_markdown(size = 11, hjust = 0),
              panel.border = element_rect(color = "black", fill = NA, size = .5))

RatingPatch_sep <- 
  RatingCor_split / RatingsDens_sep +
    plot_annotation(tag_levels = list(c("a.","b."))) &
    theme(plot.tag.position =  "topleft",
          plot.tag = element_text(size = rel(1.65)))
#ggsave("outputs/RatingPatch_sep.png", RatingPatch_sep, width = 6.49, height = 6.02, units = "in", dpi = 600)
```

```{r split}
SurveyData_Corr2_GH <- SurveyData_Corr2_split[SurveyData_Corr2_split$Setting == "Field-only (*n* = 35)",]
SurveyData_Corr2_Both <- SurveyData_Corr2_split[SurveyData_Corr2_split$Setting == "Greenhouse and field (*n* = 43)",]

CorrTableFun_GH <- function(z){
  p_tmp <- cor.test(SurveyData_Corr2_GH[,12], SurveyData_Corr2_GH[,z],
                    method = "kendall", alternative = "two.sided")$p.value
  r_tmp <- cor.test(SurveyData_Corr2_GH[,12], SurveyData_Corr2_GH[,z],
                    method = "kendall", alternative = "two.sided")$estimate
  data.frame(Outcome = colnames(SurveyData_Corr2_GH)[z], correlation = r_tmp, p.value = p_tmp,
             row.names = NULL)}

CorrTableFun_Both <- function(z){
  p_tmp <- cor.test(SurveyData_Corr2_Both[,12], SurveyData_Corr2_Both[,z],
                    method = "kendall", alternative = "two.sided")$p.value
  r_tmp <- cor.test(SurveyData_Corr2_Both[,12], SurveyData_Corr2_Both[,z],
                    method = "kendall", alternative = "two.sided")$estimate
  data.frame(Outcome = colnames(SurveyData_Corr2_Both)[z], correlation = r_tmp, p.value = p_tmp,
             row.names = NULL)}
#Overall
resultsGH <- sapply(3:11,CorrTableFun_GH,simplify = FALSE) #warning b/c <50 data-points, not an issue
resultGH_df <- do.call(rbind, resultsGH)

resultsBoth <- sapply(3:11,CorrTableFun_Both,simplify = FALSE) #warning b/c <50 data-points, not an issue
resultBoth_df <- do.call(rbind, resultsBoth)

#CCC
resultsGH2 <- sapply(13:18,CorrTableFun_GH,simplify = FALSE) #warning b/c <50 data-points, not an issue
resultGH_df2 <- do.call(rbind, resultsGH2)

resultsBoth2 <- sapply(13:18,CorrTableFun_Both,simplify = FALSE) #warning b/c <50 data-points, not an issue
resultBoth_df2 <- do.call(rbind, resultsBoth2)


Split_wb <- createWorkbook()
addWorksheet(Split_wb, "Overall_GH")
addWorksheet(Split_wb, "Overall_Both")
addWorksheet(Split_wb, "CCC_GH")
addWorksheet(Split_wb, "CCC_Both")

writeData(Split_wb, "Overall_GH", resultGH_df)
writeData(Split_wb, "Overall_Both", resultBoth_df)
writeData(Split_wb, "CCC_GH", resultGH_df2)
writeData(Split_wb, "CCC_Both", resultBoth_df2)

#saveWorkbook(Split_wb,"outputs/SplitCorrTableRaw.xlsx",overwrite = T)
```

#Example
The different number of students will come from the fact that all students submitted the challenge
```{r Comp}
GreenhouseExample23 <- read.xlsx("data/2023 Data/CoverCropChallenge_Results2023.xlsx",
                               sheet = "Greenhouse")
FieldExample23 <- read.xlsx("data/2023 Data/CoverCropChallenge_Results2023.xlsx",
                          sheet = "Outside")

GreenhouseExample23 <- drop_na(GreenhouseExample23)
FieldExample23 <- drop_na(FieldExample23)

# Keep only rows in FieldExample that match with GreenhouseExample based on 'State' and 'Name'
FieldExample23 <- semi_join(FieldExample23, GreenhouseExample23, by = c("State", "Name"))

#Order the two dfs by state and student name so that the numbering is equal
GreenhouseExample <- 
  GreenhouseExample23 %>%
  arrange(State,Name) %>% 
  mutate(Name = paste0("S",row_number()))

FieldExample <-
  FieldExample23 %>% 
  arrange(State,Name) %>% 
  mutate(Name = paste0("S",row_number()))

cbind(GreenhouseExample[,c(1,2)],FieldExample[,c(1,2)])

GreenhouseBiomass <-
  GreenhouseExample %>% 
    select(Name,ends_with(".biomass.(g/pot)")&!starts_with("Total")) %>% 
    rename_with(~gsub("\\.biomass\\.\\(g/pot\\)", "", .), everything()) %>% 
    pivot_longer(cols = -Name, names_to = "Family",values_to = "Biomass_g.pot") %>% 
    mutate(Biomass_g.m2 = Biomass_g.pot*(1550.0031/28.26), .keep = "unused") %>% #Conversion: g/pot to g/m2
    mutate(Biomass_lbs.ac = Biomass_g.m2*8.92179) %>% #Conversion: g/m2 to lbs/ac
  ggplot(.,aes(reorder(Name,Biomass_lbs.ac,sum),Biomass_lbs.ac, fill = Family))+
    geom_bar(stat = "identity")+
    viridis::scale_fill_viridis(discrete = TRUE, begin = 0, end = .9)+
    labs(x = NULL, y=expression(paste("Crop biomass (lbs ac"^-1,")",sep = "")),
         fill = NULL)+
    scale_y_continuous(labels = scales::comma)+
    theme(axis.text.x = element_text(angle = 90,vjust = .5),
          legend.position = "bottom",
          legend.text = element_text(face = "italic"))+
    facet_wrap(~"Greenhouse")

GreenhouseEvenness <-
  GreenhouseExample %>% 
    select(Name,ends_with("evenness")) %>% 
    rename(Evenness = Observed.family.evenness) %>% 
  ggplot(.,aes(reorder(Name,Evenness,sum),Evenness))+
    geom_bar(stat = "identity")+
    labs(x = NULL)+
    theme(axis.text.x = element_text(angle = 90,vjust = .5))

GreenhouseEcon <-
  GreenhouseExample %>% 
    select(Name,`Economic.efficiency.(lb/$)`) %>% 
    #mutate(`EconomicEfficiency_kg.$` = `Economic.efficiency.(lb/$)`/2.2, .keep = "unused") %>% #OFF: Conversion: lbs/$ to kg/$
    filter(`Economic.efficiency.(lb/$)` != 0) %>% 
  ggplot(.,aes(reorder(Name,`Economic.efficiency.(lb/$)`,sum),`Economic.efficiency.(lb/$)`))+
    geom_bar(stat = "identity")+
    labs(x = NULL,
         y=expression(atop("Economic efficiency",
                           paste("(lbs crop biomass dollar"^-1,")",sep = ""))))+
    scale_y_continuous(labels = scales::comma)+
    theme(axis.text.x = element_text(angle = 90,vjust = .5))


FieldBiomass <-
  FieldExample %>% 
    select(Name,ends_with(".biomass.(g/0.25m2)")&!starts_with("Total")) %>% 
    rename_with(~gsub("\\.biomass\\.\\(g/0.25m2\\)", "", .), everything()) %>% 
    pivot_longer(cols = -Name, names_to = "Family",values_to = "Biomass_g.0.25m2") %>% 
    mutate(Biomass_g.m2 = Biomass_g.0.25m2*4, .keep = "unused") %>% #Conversion: g/pot to g/m2
    mutate(Biomass_lbs.ac = Biomass_g.m2*8.92179) %>% #Conversion: g/m2 to lbs/ac
  ggplot(.,aes(reorder(Name,Biomass_lbs.ac,sum),Biomass_lbs.ac, fill = Family))+
    geom_bar(stat = "identity")+
    viridis::scale_fill_viridis(discrete = TRUE, begin = 0, end = .9)+
    labs(x = NULL, y=expression(paste("Crop biomass (lbs ac"^-1,")",sep = "")),
         fill = NULL)+
    scale_y_continuous(labels = scales::comma)+
    theme(axis.text.x = element_text(angle = 90,vjust = .5),
          legend.position = "bottom",
          legend.text = element_text(face = "italic"))+
    facet_wrap(~"Field")

FieldEvenness <-
  FieldExample %>% 
    select(Name,ends_with("evenness")) %>% 
    rename(Evenness = Observed.family.evenness) %>% 
  ggplot(.,aes(reorder(Name,Evenness,sum),Evenness))+
    geom_bar(stat = "identity")+
    labs(x = NULL)+
    theme(axis.text.x = element_text(angle = 90,vjust = .5))

FieldEcon <-
  FieldExample %>% 
    select(Name,`Economic.Efficiency.(lb/$)`) %>% 
    #mutate(`EconomicEfficiency_kg.$` = `Economic.Efficiency.(lb/$)`/2.2, .keep = "unused") %>% #OFF: Conversion: lbs/$ to kg/$
  ggplot(.,aes(reorder(Name,`Economic.Efficiency.(lb/$)`,sum),`Economic.Efficiency.(lb/$)`))+
    geom_bar(stat = "identity")+
    labs(x = NULL,
         y=expression(atop("Economic efficiency",
                           paste("(lbs crop biomass dollar"^-1,")",sep = ""))))+
    scale_y_continuous(labels = scales::comma)+
    theme(axis.text.x = element_text(angle = 90,vjust = .5))

layout <- "
AB
CC
DD
EF
GH
"

CompPatch2<-
  GreenhouseBiomass+FieldBiomass+guide_area()+plot_spacer()+
    GreenhouseEvenness+FieldEvenness+GreenhouseEcon+FieldEcon+
    plot_layout(axis_titles = "collect", guides = "collect", design = layout,
                heights = c(1,.18,.0005,1,1))&
    labs(x="Student")&
    theme(legend.position = "bottom")
#ggsave("outputs/CompPatch.png",CompPatch2,width = 6.6, height = 6.2, units = "in", dpi = 600)
```

```{r Tables}
TableExample23 <- read.xlsx("data/2023 Data/CoverCropChallenge_Results2023.xlsx",
                               sheet = "Seeding rate (lbs ac)")
TableExample23 <- drop_na(TableExample23)
TableExample23 <- semi_join(TableExample23, GreenhouseExample23, by = c("State", "Name")) #sub-setting to get the same students as the plots

#Note that units are already in lbs/ac
TableExample <- 
  TableExample23 %>% 
  select(-starts_with("Total")) %>% 
  clean_names(case = "sentence") %>% 
  #mutate(across(where(is.numeric), ~round(.*1.12085,0))) %>%  #OFF: Conversion from lbs/ac to kg/ha
  arrange(State,Name) %>% #Arranging to get the same order as the other plots
  mutate(Name = paste0("S",row_number()))

TableExample_GBiomass <-
  TableExample %>% 
  select(-State) %>% 
  filter(Name %in% c("S19","S15","S17"))

TableExample_FBiomass <-
  TableExample %>% 
  select(-State) %>% 
  filter(Name %in% c("S13","S4","S7"))


#Final formatting done in Excel - gt table is cool but a waist of time!
#Saved as CompTable.xlsx in Figsures&Tables>Raw using copy and paste from a word doc. Transferred to inkscape as a pdf
library(gt)
bind_rows(mutate(TableExample_GBiomass,
                 Setting = "Greenhouse cover crop biomass - top three students"),
          mutate(TableExample_FBiomass,
                 Setting = "Field cover crop biomass - top three students")) %>% 
  select(Name,Setting,11:12,6:10,2:5,13) %>% 
  group_by(Setting) %>% 
  rename("Student name" = Name) %>% 
  gt() %>% 
  tab_spanner(label = "Brassicaceae",columns = 3:4) %>% #Familes
  tab_spanner(label = "Fabaceae",columns = 5:9) %>% 
  tab_spanner(label = "Poaceae",columns = 10:13) %>% 
  tab_spanner(label = "Polygonaceae",columns = 14) %>% 
  tab_style(
    style = cell_text(align = "center",v_align = "middle"),
    locations = list(cells_column_labels(),cells_body())) %>% #Centering columns
  tab_style(
    style = cell_text(align = "left",weight = "bold",v_align = "middle"),
    locations = list(cells_column_labels("Student name"),cells_body("Student name"))) %>% #Offset name colunm
  cols_label("Student name" = "") %>% 
  tab_style(
    style = cell_text(whitespace = "pre-wrap"),
    locations = list(cells_column_labels())) %>% #wrapping species
  tab_style(
    style = cell_text(weight = "normal",style = "italic"),
    locations = list(cells_row_groups(),cells_column_spanners())) %>% #italicizing groups
  tab_header( #Title
    title = md("Seeding rates (lbs ac<sup>-1</sup>)")) %>% 
  opt_align_table_header(align = "center") %>% 
  tab_options(table_body.hlines.color = "transparent", #removing row lines
              row_group.border.top.width = 0,row_group.border.bottom.width = 0, #removing row group lines
              table.font.size = "68%",
              table.width = "80%",
              heading.padding = px(1.5), column_labels.padding = px(1.5),
              row_group.padding = px(5), data_row.padding = px(1.5)) #%>%
  #gtsave("outputs/test2.docx")
```


```{r Spider}
SpiderExample23 <- read.xlsx("data/2023 Data/CoverCropChallenge_Results2023.xlsx",
                               sheet = "Ecosystem services axes")
SpiderExample23 <- drop_na(SpiderExample23) #remove MSU (MI) students
SpiderExample23 <- semi_join(SpiderExample23, GreenhouseExample23, by = c("State", "Name")) #sub-setting to get the same students as the plots

SpiderExample <- 
  SpiderExample23 %>% 
  clean_names(case = "sentence") %>% 
  arrange(State,Name) %>% #Arranging to get the same order as the other plots
  mutate(Name = paste0("S",row_number()))

SpiderFun <- function(x) {
  fmsb::radarchart(x,axistype=1,
                   pcol=rgb(0.2,0.5,0.5,0.9) , pfcol=rgb(0.2,0.5,0.5,0.5),plwd=2,
                   cglcol="grey", cglty=1,
                   axislabcol="grey10",caxislabels=seq(1,5,1), cglwd=0.8,
                   vlcex=1)}

##Top 3 (least to most): S7, S4, S13
SpiderExample_S7a <- SpiderExample[SpiderExample$Name == "S7",-c(1:2)] #Student S7
SpiderExample_S13a <- SpiderExample[SpiderExample$Name == "S13",-c(1:2)] #Student S13

SpiderExample_S7b <- rbind(rep(5,8) , rep(1,8), SpiderExample_S7a)
SpiderExample_S13b <- rbind(rep(5,8) , rep(1,8),SpiderExample_S13a)  
  
png("SpiderPlot.png",width = 9.75, height = 5.12, units = "in", res = 600)
par(mfrow = c(1, 2),mar = c(5, 1, 4, 1) + 0.1)
  SpiderFun(SpiderExample_S7b)+title("Student 7",adj = 0,line = 1)
  SpiderFun(SpiderExample_S13b)+title("Student 13",adj = 0,line = 1)
dev.off()
```

# Range
```{r}
#2022 prep
GreenhouseRange22 <- read.xlsx("data/2022 Data/CoverCropChallenge_Results2022.xlsx",
                               sheet = "Greenhouse")
FieldRange22 <- read.xlsx("data/2022 Data/CoverCropChallenge_Results2022.xlsx",
                          sheet = "Outside")

GreenhouseRange22 <- drop_na(GreenhouseRange22) %>% mutate(Year = "2022", .before = State)
FieldRange22 <- drop_na(FieldRange22) %>% mutate(Year = "2022", .before = State)


#2023 prep
GreenhouseRange23 <- read.xlsx("data/2023 Data/CoverCropChallenge_Results2023.xlsx",
                               sheet = "Greenhouse")
FieldRange23 <- read.xlsx("data/2023 Data/CoverCropChallenge_Results2023.xlsx",
                          sheet = "Outside")

GreenhouseRange23 <- drop_na(GreenhouseRange23) %>% mutate(Year = "2023", .before = State)
FieldRange23 <- drop_na(FieldRange23) %>% mutate(Year = "2023", .before = State)

#Merging
compare_df_cols(GreenhouseRange22,GreenhouseRange23)
GreenhouseRange <- rbind(GreenhouseRange22,GreenhouseRange23)
GreenhouseRange <- GreenhouseRange %>% 
  select("Year","Name",
         "Total.biomass.(lb/a)","Observed.family.evenness","Economic.efficiency.(lb/$)") %>% 
  mutate(Setting = "Greenhouse")


compare_df_cols(FieldRange22,FieldRange23)
FieldRange <- rbind(FieldRange22,FieldRange23)
FieldRange <- FieldRange %>% 
  select("Year","Name",
         "Total.biomass.(lb/acre)","Observed.family.evenness","Economic.Efficiency.(lb/$)") %>% 
  rename("Total.biomass.(lb/a)" = "Total.biomass.(lb/acre)",
         "Economic.efficiency.(lb/$)" = "Economic.Efficiency.(lb/$)") %>% 
  mutate(Setting = "Field")

compare_df_cols(GreenhouseRange,FieldRange)
RangeData <- rbind(GreenhouseRange,FieldRange)

#Calculating range and converting
RangeSum <- 
  RangeData %>%
    select(-Name) %>% 
    rename("Total biomass (lb/a)" = "Total.biomass.(lb/a)",
           "Evenness" = "Observed.family.evenness",
           "Economic efficiency (lb/$)" = "Economic.efficiency.(lb/$)" ) %>% 
    mutate("Total biomass (kg/ha)" = `Total biomass (lb/a)`*1.12085,  #converting to kg/ha
           "Economic efficiency (kg/$)" = `Economic efficiency (lb/$)`*0.453592) %>%  #converting to $/ha
    select(Year,"Total biomass (kg/ha)",Evenness,"Economic efficiency (kg/$)",Setting) %>%  #getting rid of old
    group_by(Setting,Year) %>% 
    summarise(across(everything(),list(min = min, max = max)))

#Presenting the range in a nice table layout
RangeSumTab<-
  RangeSum %>% 
  pivot_longer(cols = -c(Setting,Year),
               names_to = c("Variable","Calc"), names_sep = "_",
               values_to = "Value") %>% 
  pivot_wider(names_from = Calc,
              values_from = Value)

RangeSumTab$Setting <- factor(RangeSumTab$Setting,levels = c("Greenhouse","Field")) #factor so greenhouse first

RangeSumTab %>%
  pivot_wider(names_from = Setting, #one more pivot for spanners in gt()
              values_from = c(min,max),
              names_glue = "{Setting}_{.value}", #specifying order for gt()
              names_vary = "slowest",
              names_sort = TRUE) %>% 
  gt(groupname_col = "Year",row_group_as_column = TRUE) %>% 
  tab_spanner_delim(delim = "_") %>% 
  fmt_number(rows = c(1,4), decimals = 0) %>% #rounding biomass
  fmt_number(rows = c(2,5), decimals = 2) %>% #rounding evenness
  fmt_number(rows = c(3,6), decimals = 2) #rounding econ. eff.
```

pot values in paper
```{r eval=FALSE, include=FALSE}
# GreenhouseRange %>% 
#   group_by(Year) %>% 
#   select(Year, State, Name,
#          `Total.biomass.(g/pot)`,
#          `Total.biomass.(lb/a)`) %>% 
#   slice_max(`Total.biomass.(g/pot)`, n=1) %>% 
#   mutate(`Total.biomass.(kg/ha)` = `Total.biomass.(lb/a)` * 1.12085)

# GreenhouseRange %>% 
#   group_by(Year) %>% 
#   select(Year, State, Name,
#          `Total.biomass.(g/pot)`,
#          `Total.biomass.(lb/a)`) %>% 
#   slice_min(`Total.biomass.(g/pot)`, n=1) %>% 
#   mutate(`Total.biomass.(kg/ha)` = `Total.biomass.(lb/a)` * 1.12085)
```

